---
title: "External Report"
author: "Steven Pappas and Gregory J. Matthews"
format: pdf
execute:
  echo: false
  message: false
  warning: false
editor: visual
date: "May 20, 2026"
---

This analysis seeks to evaluate the probability of a connection (i.e. an Embassy) between an African country and an external country, which could also be an African country as a function of democracy score.  We used democracy scores from Freedom House (TOTLIB1) and the POLITY IV database (POLITY and POLITY2).

This main analyses were split into two parts: a reduced model and a full model. The reduced model only considers democracy as a fixed effect, while including random intercepts for the internal country, the external country, their interaction, and the year. These random effects account for correlation between observations with in the structure of the data. 

The full model includes all of the parts of the reduced model, but also includes the external country's population, GNI, official development assistance gross (ODAG), and trade import gross (TRDIM). We applied a log transformation to each of these new variables due to their fairly extreme right-skewness (shown below as density plots). Finally, we applied both of these model with lagged democracy scores of 1, 2, and 3 years.  

# Reduced Model

$Y_{ijk}$ is a 1 if there is a connection between African country $i$ and external country $j$ in year $k$ and 0 otherwise.  Then we build the following model with $X_{1jk}$ as the democracy score of external country $j$ in year $k$: 

$$
Y_{ijk} \sim \text{Binomial}(1, p_{ijk})
$$

$$
\text{logit}(p_{ijk}) = \beta_0 + \beta_1X_{1jk} + \gamma_{0i} + \gamma_{0j} + \gamma_{0ij} + \gamma_{0k} + \epsilon_{ijk}
$$

$$
\gamma_{0i} \sim \text{N}(0, \sigma_i^2)
$$

$$
\gamma_{0j} \sim \text{N}(0, \sigma_j^2)
$$

$$
\gamma_{0ij} \sim \text{N}(0, \sigma_{ij}^2)
$$

$$
\gamma_{0k} \sim \text{N}(0, \sigma_k^2)
$$

In lagged models, the year $k$ changes units depending on the lag. For instance, a one-year lag would produce the model equation $\text{logit}(p_{ijk}) = \beta_0 + \beta_1X_{1j(k-1)} + \gamma_{0i} + \gamma_{0j} + \gamma_{0ij} + \gamma_{0k} + \epsilon_{ijk}$, where $X_{1j(k-1)}$ is the external country's democracy score in the prior year (i.e. year $k$-1).

As shown in Table 1, all external country democracy scores and their lags show significance at the $\alpha$ = 0.05 level. Interestingly, each model's $\hat{\beta}$ coefficients indicate that the more democratic external country $j$ is, the less likely they are to have an embassy relationship with internal country $i$. For instance, a one-unit increase in unlagged TOTLIB1 (where a higher score indicates a less democratic country) increases the odds of an embassy relationship by a factor of $e^{0.185}$ = 1.203, approximately a 20% increase in the odds of a embassy relationship.

# Full Model

$$
Y_{ijk} \sim \text{Binomial}(1, p_{ijk})
$$

$$
\text{logit}(p_{ijk}) = \beta_0 + \beta_1X_{1jk} + \ldots + \beta_4X_{4ijk} + \gamma_{0i} + \gamma_{0j} + \gamma_{0ij} + \gamma_{0k} + \epsilon_{ijk}
$$

$$
\gamma_{0i} \sim \text{N}(0, \sigma_i^2)
$$

$$
\gamma_{0j} \sim \text{N}(0, \sigma_j^2)
$$

$$
\gamma_{0ij} \sim \text{N}(0, \sigma_{ij}^2)
$$

$$
\gamma_{0k} \sim \text{N}(0, \sigma_k^2)
$$

Our full model equations largely follow the same setup as the reduced model with the addition of the aforementioned log-transformed external country characteristics.  Note that the external democracy score, the external country population, and the external country GNI are all attributes of the external country only, whereas ODAG, imports, and exports are attributes of the pair of countries.  

As shown in Table 2, the only significant variable at the $\alpha$ = 0.05 level is the two-year lagged TOTLIB1 score. Additionally, the democracy score's effect sizes, as shown by their $\hat{\beta}$ coefficients, are much smaller than their reduced model counterparts and the single instance of significance (two-year lagged TOTLIB) is in the opposite direction of the reduced model. Specifically this means that a one-unit increase in the two-year lagged TOTLIB1 score (i.e. the country gets less democratic) decreases the odds of an embassy relationship by a factor of 0.983, or a 1.7 percent decrease in the odds.  

Table 3 shows results without ODAG included in the model. With the data that we have there is no ODAG values fro African external countries, and thus the only external countries included in the model are non-African countries.  Practically, this means that African-African connections are never considered. By dropping ODAG from the model, these possible connections are kept.  In this case, we have mony more complete observations and POLITY and POLITY2 show up as significant in the same direction as in the reduced model, though the effects sizes are smaller than the reduced model as the additional covariates explain significant amount of variability in the response.  

```{r}

library(tidyverse)
library(readxl)
library(data.table)

masterset = read_csv("data2026/MASTER DATASET 3.26.2026.csv")

restofworld = read_excel("data2026/Rest of the World - 5.6.2026.xlsx")

masterset = masterset %>%
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         across(where(is.numeric), ~ na_if(., -88)),
         across(where(is.numeric), ~ na_if(., -77)),
         across(where(is.numeric), ~ na_if(., -66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY))

masterset$GNI <- gsub(",",".",masterset$GNI)
masterset$GNI <- gsub(" ","",masterset$GNI)%>% as.numeric()

masterset$GNI_CAP <- gsub(",",".",masterset$GNI_CAP)
masterset$GNI_CAP <- gsub(" ","",masterset$GNI_CAP)%>% as.numeric()

masterset$POPULATN <- gsub(",",".",masterset$POPULATN)
masterset$POPULATN <- gsub(" ","",masterset$POPULATN) %>% as.numeric()

names(masterset)[which(names(masterset) == "TRDX352b")] <- "TRDEX352b"
names(masterset)[which(names(masterset) == "TRDX200h")] <- "TRDEX200h"
names(masterset)[which(names(masterset) == "TRDX200m")] <- "TRDEX200m"
names(masterset)[which(names(masterset) == "TDX321sr")] <- "TRDEX321sr"
names(masterset)[which(names(masterset) == "TDX321sm")] <- "TRDEX321sm"
names(masterset)[which(names(masterset) == "TDX321yr")] <- "TRDEX321yr"

names(masterset)[which(names(masterset) == "TRDI200h")] <- "TRDIM200h"
names(masterset)[which(names(masterset) == "TRDI200m")] <- "TRDIM200m"
names(masterset)[which(names(masterset) == "TDI321sr")] <- "TRDIM321sr"
names(masterset)[which(names(masterset) == "TDI321sm")] <- "TRDIM321sm"
names(masterset)[which(names(masterset) == "TDI321yr")] <- "TRDIM321yr"
names(masterset)[which(names(masterset) == "TDI316SU")] <- "TRDIM316su"

restofworld <- restofworld %>% 
  rename(v2x_LIBDEM = V2x_Libdem) %>%
  mutate(GNI = as.numeric(GNI),
         GNI_CAP = as.numeric(GNI_CAP),
         AVLIFEEX = as.numeric(AVLIFEEX),
         ENRGUSE = as.numeric(ENRGUSE)) %>% 
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         across(where(is.numeric), ~ na_if(., -88)),
         across(where(is.numeric), ~ na_if(., -77)),
         across(where(is.numeric), ~ na_if(., -66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY))

restofworld$GNI <- gsub(",",".",restofworld$GNI)
restofworld$GNI <- gsub(" ","",restofworld$GNI)%>% as.numeric()

restofworld$GNI_CAP <- gsub(",",".",restofworld$GNI_CAP)
restofworld$GNI_CAP <- gsub(" ","",restofworld$GNI_CAP)%>% as.numeric()

restofworld$POPULATN <- gsub(",",".",restofworld$POPULATN)
restofworld$POPULATN <- gsub(" ","",restofworld$POPULATN) %>% as.numeric()

countrycodes <- list(
  world = restofworld %>%
    select(CCODE:COUNTRY) %>%
    unique(),
  africa = masterset %>%
    select(CCODE:COUNTRY) %>%
    mutate(CCODE = paste0("C", CCODE)) %>%
    unique()
) %>%
  rbindlist()

external_democracy <- list(
  world = restofworld %>%
    select(CCODE,YEAR,TOTLIB1, POLITY, POLITY2, v2x_LIBDEM, GNI, GNI_CAP, POPULATN) %>%
    unique(),
  africa = masterset %>%
    select(CCODE,YEAR,TOTLIB1, POLITY, POLITY2, GNI, GNI_CAP, POPULATN) %>% # WHERE IS INTERNAL V2X?
    mutate(CCODE = paste0("C", CCODE)) %>%
    unique()
) %>%
  rbindlist(fill = T)

countrycodes <- countrycodes %>% 
  mutate(CCODE = ifelse(CCODE == "C99","C099",CCODE))

external_democracy <- external_democracy %>% 
  mutate(CCODE = ifelse(CCODE == "C99","C099",CCODE)) %>%
  rename_with(
    .fn = ~ paste0(.x, "_EXT"),
    .cols = -YEAR
  ) %>%
  arrange(CCODE_EXT, YEAR) %>% 
  group_by(CCODE_EXT)  %>% 
  mutate(TOTLIB1_EXT_lag1 = lag(TOTLIB1_EXT,1),
         TOTLIB1_EXT_lag2 = lag(TOTLIB1_EXT,2),
         TOTLIB1_EXT_lag3 = lag(TOTLIB1_EXT,3),
         POLITY_EXT_lag1 = lag(POLITY_EXT,1),
         POLITY_EXT_lag2 = lag(POLITY_EXT,2),
         POLITY_EXT_lag3 = lag(POLITY_EXT,3),
         POLITY2_EXT_lag1 = lag(POLITY2_EXT,1),
         POLITY2_EXT_lag2 = lag(POLITY2_EXT,2),
         POLITY2_EXT_lag3 = lag(POLITY2_EXT,3),
         v2x_LIBDEM_EXT_lag1 = lag(v2x_LIBDEM_EXT,1),
         v2x_LIBDEM_EXT_lag2 = lag(v2x_LIBDEM_EXT,2),
         v2x_LIBDEM_EXT_lag3 = lag(v2x_LIBDEM_EXT,3)
  ) %>% 
  ungroup()

newdata <- masterset %>%
  select(CCODE_INT = CCODE, COUNTRY_INT = COUNTRY, YEAR, C099:C572) %>%
  mutate(CCODE_INT = paste0("C", CCODE_INT)) %>%
  pivot_longer(!CCODE_INT:YEAR, names_to = "CCODE_EXT", values_to = "CONNECTION") %>%
  left_join(countrycodes, by = c("CCODE_EXT" = "CCODE"), relationship = "many-to-many") %>%
  select(CONNECTION, CCODE_INT, COUNTRY_INT, CCODE_EXT, COUNTRY_EXT = COUNTRY, 
         everything()) %>%
  filter(CONNECTION %in% c(0, 1), CCODE_INT != CCODE_EXT) %>% 
  left_join(external_democracy, by = c("CCODE_EXT","YEAR" = "YEAR")) %>%
  mutate(GNI_EXT = as.numeric(GNI_EXT),
         GNI_CAP_EXT = as.numeric(GNI_CAP_EXT))

odag_data <- masterset %>% rename(ODAG251 = odag251) %>% 
  select(CCODE_INT = CCODE, COUNTRY_INT = COUNTRY, YEAR, ODAG201:ODAG643, ODAG251) %>% 
  mutate(across(c(ODAG201:ODAG643,ODAG251), ~ gsub(",", ".", .x))) %>% 
  mutate(across(c(ODAG201:ODAG643,ODAG251), as.numeric)) %>% 
  pivot_longer(cols = c(ODAG201:ODAG643,ODAG251), names_to ="CCODE_EXT", values_to = "ODAG") %>% 
  mutate(CCODE_EXT = gsub( "ODAG","",CCODE_EXT)) %>%
  mutate(CCODE_EXT = paste0("C", CCODE_EXT),
         CCODE_INT = paste0("C", CCODE_INT)) %>% 
  filter(CCODE_INT != "CNA" & ODAG != -99)

trdex_data <- masterset %>% 
  select(CCODE_INT = CCODE, 
         COUNTRY_INT = COUNTRY, 
         YEAR, 
         matches("^TRDEX\\d{3}")) %>% 
  mutate(across(TRDEX351:TRDEX203, ~ gsub(",", ".", .x))) %>% 
  mutate(across(TRDEX351:TRDEX203, as.numeric)) %>% 
  mutate(TRDEX200 = ifelse((is.na(TRDEX200) &
                              is.na(TRDEX200h) &
                              is.na(TRDEX200h)),
                           NA,
                           rowSums(across(c(TRDEX200, TRDEX200h, TRDEX200m)), na.rm = TRUE)
  )) %>%
  mutate(TRDEX321 = ifelse((is.na(TRDEX321sm) &
                              is.na(TRDEX321sr) &
                              is.na(TRDEX321yr)),
                           NA,
                           rowSums(across(c(TRDEX321sm, TRDEX321sr, TRDEX321yr)), na.rm = TRUE)
  )) %>% #combining 321 yr, sm, se
  pivot_longer(cols = TRDEX351:TRDEX321, names_to ="CCODE_EXT", values_to = "TRDEX") %>%
  mutate(CCODE_EXT = gsub( "TRDEX","",CCODE_EXT)) %>% 
  mutate(CCODE_EXT = paste0("C", CCODE_EXT),
         CCODE_INT = paste0("C", CCODE_INT)) %>% 
  filter(CCODE_INT != "CNA")

trdim_data <- masterset %>% 
  select(CCODE_INT = CCODE, 
         COUNTRY_INT = COUNTRY, 
         YEAR, 
         matches("^TRDIM\\d{3}")) %>% 
  mutate(across(TRDIM351:TRDIM203, ~ gsub(",", ".", .x))) %>% 
  mutate(across(TRDIM351:TRDIM203, as.numeric)) %>% 
  mutate(TRDIM200 = ifelse((is.na(TRDIM200) &
                              is.na(TRDIM200h) &
                              is.na(TRDIM200h)),
                           NA,
                           rowSums(across(c(TRDIM200, TRDIM200h, TRDIM200m)), na.rm = TRUE)
  )) %>% #summing 200, 200m, 200h to combine China
  mutate(TRDIM321 = ifelse((is.na(TRDIM321sm) &
                              is.na(TRDIM321sr) &
                              is.na(TRDIM321yr)),
                           NA,
                           rowSums(across(c(TRDIM321sm, TRDIM321sr, TRDIM321yr)), na.rm = TRUE)
  )) %>% #combining 321 yr, sm, se
  mutate(TRDIM316 = ifelse((is.na(TRDIM316) &
                              is.na(TRDIM316su)),
                           NA,
                           rowSums(across(c(TRDIM316,TRDIM316su)), na.rm = TRUE)
  )) %>% #combining 316 and 316su (i.e. Russia and Soviet Union)
  pivot_longer(cols = TRDIM351:TRDIM321, names_to ="CCODE_EXT", values_to = "TRDIM") %>% 
  mutate(CCODE_EXT = gsub( "TRDIM","",CCODE_EXT)) %>%
  mutate(CCODE_EXT = paste0("C", CCODE_EXT),
         CCODE_INT = paste0("C", CCODE_INT)) %>% 
  filter(CCODE_INT != "CNA") %>% filter(!(CCODE_INT == "C114" & CCODE_EXT == "C148" & YEAR == 1972))

cleandata <- newdata %>% 
  left_join(odag_data %>% select(CCODE_INT,YEAR,CCODE_EXT,ODAG), 
            by = c("CCODE_INT","CCODE_EXT","YEAR")) %>%
  left_join(trdex_data %>% select(CCODE_INT,YEAR,CCODE_EXT,TRDEX), 
            by = c("CCODE_INT","CCODE_EXT","YEAR")) %>%
  left_join(trdim_data %>% select(CCODE_INT,YEAR,CCODE_EXT,TRDIM), 
            by = c("CCODE_INT","CCODE_EXT","YEAR")) %>% 
  mutate( ODAG = ifelse(ODAG == -99, NA, ODAG),
         TRDIM = ifelse(TRDIM == -99, NA, TRDIM),
         TRDEX = ifelse(TRDEX == -99, NA, TRDEX),
         GNI_EXT = ifelse(GNI_EXT == -99, NA, GNI_EXT),
         POPULATN_EXT = ifelse(POPULATN_EXT == -99, NA, POPULATN_EXT),
          logGNI_EXT = log(GNI_EXT, 10),
         logPOP_EXT = log(POPULATN_EXT, 10),
         logODAG = log(ODAG+1,10),
         logTRDIM = log(TRDIM+1,10),
         logTRDEX = log(TRDEX+1,10)
        ) %>% ungroup() 

```
Below we look at the distributions of predictor variables in the full model.  

```{r}
cleandata %>% 
  ggplot(aes(x = POPULATN_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Population Density\n of External Countries",
    x = "External Country Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
cleandata %>% 
  ggplot(aes(x = logPOP_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Population\n Density of External Countries",
    x = "Log-Transformed External Country Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
cleandata %>% 
  ggplot(aes(x = GNI_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Gross National Income (GNI)\n Density of External Countries",
    x = "External Country GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
cleandata %>% 
  ggplot(aes(x = logGNI_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Gross National Income (GNI)\n Density of External Countries",
    x = "Log-Transformed External Country GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
cleandata %>% 
  ggplot(aes(x = ODAG)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Official Development Assistance Gross (ODAG)\n Density of External Countries",
    x = "External Country ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
cleandata %>% 
  ggplot(aes(x = logODAG)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Official Development Assistance Gross\n (ODAG) Density of External Countries",
    x = "Log-Transformed External Country ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
cleandata %>% 
  ggplot(aes(x = TRDIM)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Total Import (TRDIM)\n Density of External Countries",
    x = "External Country TRDIM"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
cleandata %>% 
  ggplot(aes(x = logTRDIM)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Total Import (TRDIM)\n Density of External Countries",
    x = "Log-Transformed External Country TRDIM"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

<!-- ```{r} -->
<!-- interaction <- cleandata %>% -->
<!--   group_by(CCODE_INT, COUNTRY_INT, CCODE_EXT, COUNTRY_EXT) %>% -->
<!--   reframe(N = n()) -->

<!-- interaction2 <- list( -->
<!--   world = restofworld %>% -->
<!--     select(CCODE_EXT = CCODE, COUNTRY_EXT = COUNTRY) %>% -->
<!--     unique(), -->
<!--   africa = masterset %>% -->
<!--     mutate(CCODE_INT = paste0("C", CCODE)) %>% -->
<!--     select(CCODE_INT, COUNTRY_INT = COUNTRY) %>% -->
<!--     unique() -->
<!-- ) %>% -->
<!--   reduce(merge, by = NULL) %>% -->
<!--   left_join(interaction, by = c("CCODE_INT", "COUNTRY_INT", "CCODE_EXT", "COUNTRY_EXT")) %>% -->
<!--   mutate(N = ifelse(is.na(N), 0, N)) -->

<!-- table(interaction2$N) -->

<!-- round(table(interaction2$N)/nrow(interaction2)*100, 1) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- cleandata %>% -->
<!--   mutate(CONNECTION = as.factor(CONNECTION)) %>% -->
<!--   ggplot(aes(x = CONNECTION, y = TOTLIB1_EXT)) + -->
<!--   geom_boxplot() + -->
<!--   scale_y_continuous(limits = c(0, 15)) + -->
<!--   facet_wrap(~YEAR) + -->
<!--   labs( -->
<!--     title = "Boxplot of External Country TOTLIB1 by External-Internal Country Connection and Year", -->
<!--     x = "External-Internal Country Connection", -->
<!--     y = "External Country TOTLIB1" -->
<!--   ) + -->
<!--   theme_bw() + -->
<!--   theme( -->
<!--     plot.title = element_text(hjust = 0.5, face = "bold") -->
<!--   ) -->

<!-- cleandata %>% -->
<!--   mutate(CONNECTION = as.factor(CONNECTION)) %>% -->
<!--   ggplot(aes(x = CONNECTION, y = POLITY_EXT)) + -->
<!--   geom_boxplot() + -->
<!--   scale_y_continuous(limits = c(-10, 10)) + -->
<!--   facet_wrap(~YEAR) + -->
<!--   labs( -->
<!--     title = "Boxplot of External Country POLITY by External-Internal Country Connection and Year", -->
<!--     x = "External-Internal Country Connection", -->
<!--     y = "External Country POLITY" -->
<!--   ) + -->
<!--   theme_bw() + -->
<!--   theme( -->
<!--     plot.title = element_text(hjust = 0.5, face = "bold") -->
<!--   ) -->

<!-- cleandata %>% -->
<!--   mutate(CONNECTION = as.factor(CONNECTION)) %>% -->
<!--   ggplot(aes(x = CONNECTION, y = POLITY2_EXT)) + -->
<!--   geom_boxplot() + -->
<!--   scale_y_continuous(limits = c(0, 15)) + -->
<!--   facet_wrap(~YEAR) + -->
<!--   labs( -->
<!--     title = "Boxplot of External Country POLITY2 by External-Internal Country Connection and Year", -->
<!--     x = "External-Internal Country Connection", -->
<!--     y = "External Country POLITY2" -->
<!--   ) + -->
<!--   theme_bw() + -->
<!--   theme( -->
<!--     plot.title = element_text(hjust = 0.5, face = "bold") -->
<!--   ) -->

<!-- ``` -->
Below are the correlations between the predictors in the full model.  

```{r}
cordata <- cleandata %>%
  select(logPOP_EXT, logGNI_EXT, logODAG, logTRDIM, YEAR) %>%
  drop_na()

cat("Pearson Correlation")

cor(cordata, method = "pearson")

cat("Kendall-Tau Correlation")

cor(cordata, method = "kendall")

cat("Spearman Correlation")

cor(cordata, method = "spearman")

```

```{r}
library(lme4)

load("externalmodels2026/mod0_TOTLIB1.RData")

load("externalmodels2026/mod0_TOTLIB1_lag1.RData")

load("externalmodels2026/mod0_TOTLIB1_lag2.RData")

load("externalmodels2026/mod0_TOTLIB1_lag3.Rdata")

load("externalmodels2026/mod0_POLITY.Rdata")

load("externalmodels2026/mod0_POLITY_lag1.Rdata")

load("externalmodels2026/mod0_POLITY_lag2.Rdata")

load("externalmodels2026/mod0_POLITY_lag3.Rdata")

load("externalmodels2026/mod0_POLITY2.Rdata")

load("externalmodels2026/mod0_POLITY2_lag1.Rdata")

load("externalmodels2026/mod0_POLITY2_lag2.Rdata")

load("externalmodels2026/mod0_POLITY2_lag3.Rdata")

load("externalmodels2026/mod0_v2x_LIBDEM.Rdata")

load("externalmodels2026/mod0_v2x_LIBDEM_lag1.Rdata")

load("externalmodels2026/mod0_v2x_LIBDEM_lag2.Rdata")

load("externalmodels2026/mod0_v2x_LIBDEM_lag3.Rdata")

```

```{r}
library(gt)

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1))) %>% rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_TOTLIB1, parm = "TOTLIB1_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod0_TOTLIB1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_TOTLIB1_lag1, parm = "TOTLIB1_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod0_TOTLIB1_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_TOTLIB1_lag2, parm = "TOTLIB1_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod0_TOTLIB1_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_TOTLIB1_lag3, parm = "TOTLIB1_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod0_TOTLIB1_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY, parm = "POLITY_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod0_POLITY)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY_lag1, parm = "POLITY_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod0_POLITY_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY_lag2, parm = "POLITY_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod0_POLITY_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY_lag3, parm = "POLITY_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod0_POLITY_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY2, parm = "POLITY2_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod0_POLITY2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY2_lag1, parm = "POLITY2_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod0_POLITY2_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY2_lag2, parm = "POLITY2_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod0_POLITY2_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_POLITY2_lag3, parm = "POLITY2_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod0_POLITY2_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_v2x_LIBDEM))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_v2x_LIBDEM, parm = "v2x_LIBDEM_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod0_v2x_LIBDEM)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_v2x_LIBDEM_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_v2x_LIBDEM_lag1, parm = "v2x_LIBDEM_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod0_v2x_LIBDEM_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_v2x_LIBDEM_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_v2x_LIBDEM_lag2, parm = "v2x_LIBDEM_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod0_v2x_LIBDEM_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_v2x_LIBDEM_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod0_v2x_LIBDEM_lag3, parm = "v2x_LIBDEM_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod0_v2x_LIBDEM_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3, v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "POLITY") ~ "POLITY",
                         str_detect(var, "v2x_LIBDEM") ~ "v2x_LIBDEM"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    n = md("$n$"),
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 1: Reduced Model Parameters for External **Democracy Scores** and Their **Lags**")
  )

```

 
```{r}

load("externalmodels2026/mod1_TOTLIB1.Rdata")

load("externalmodels2026/mod1_TOTLIB1_lag1.Rdata")

load("externalmodels2026/mod1_TOTLIB1_lag2.Rdata")

load("externalmodels2026/mod1_TOTLIB1_lag3.Rdata")

load("externalmodels2026/mod1_POLITY.Rdata")

load("externalmodels2026/mod1_POLITY_lag1.Rdata")

load("externalmodels2026/mod1_POLITY_lag2.Rdata")

load("externalmodels2026/mod1_POLITY_lag3.Rdata")

load("externalmodels2026/mod1_POLITY2.Rdata")

load("externalmodels2026/mod1_POLITY2_lag1.Rdata")

load("externalmodels2026/mod1_POLITY2_lag2.Rdata")

load("externalmodels2026/mod1_POLITY2_lag3.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM_lag1.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM_lag2.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM_lag3.Rdata")

```

```{r}

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1, parm = "TOTLIB1_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_TOTLIB1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag1, parm = "TOTLIB1_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_TOTLIB1_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag2, parm = "TOTLIB1_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_TOTLIB1_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag3, parm = "TOTLIB1_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_TOTLIB1_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY, parm = "POLITY_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_POLITY)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY_lag1, parm = "POLITY_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_POLITY_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY_lag2, parm = "POLITY_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_POLITY_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY_lag3, parm = "POLITY_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_POLITY_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2, parm = "POLITY2_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_POLITY2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag1, parm = "POLITY2_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_POLITY2_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag2, parm = "POLITY2_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_POLITY2_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag3, parm = "POLITY2_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_POLITY2_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM, parm = "v2x_LIBDEM_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_v2x_LIBDEM)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag1, parm = "v2x_LIBDEM_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_v2x_LIBDEM_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag2, parm = "v2x_LIBDEM_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_v2x_LIBDEM_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag3, parm = "v2x_LIBDEM_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_v2x_LIBDEM_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3, v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "POLITY") ~ "POLITY",
                         str_detect(var, "v2x_LIBDEM") ~ "v2x_LIBDEM"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    n = md("$n$"),
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 2: Full Model Parameters for External **Democracy Scores** and Their **Lags**")
  )

```

```{r}

load("externalmodels2026/mod1_TOTLIB1_noODAG.Rdata")

load("externalmodels2026/mod1_TOTLIB1_lag1_noODAG.Rdata")

load("externalmodels2026/mod1_TOTLIB1_lag2_noODAG.Rdata")

load("externalmodels2026/mod1_TOTLIB1_lag3_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY_lag1_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY_lag2_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY_lag3_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY2_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY2_lag1_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY2_lag2_noODAG.Rdata")

load("externalmodels2026/mod1_POLITY2_lag3_noODAG.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM_noODAG.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM_lag1_noODAG.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM_lag2_noODAG.Rdata")

load("externalmodels2026/mod1_v2x_LIBDEM_lag3_noODAG.Rdata")

```

```{r}

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_noODAG, parm = "TOTLIB1_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_TOTLIB1_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag1_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag1_noODAG, parm = "TOTLIB1_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_TOTLIB1_lag1_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag2_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag2_noODAG, parm = "TOTLIB1_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_TOTLIB1_lag2_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag3_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag3_noODAG, parm = "TOTLIB1_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_TOTLIB1_lag3_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY_noODAG, parm = "POLITY_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_POLITY_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag1_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY_lag1_noODAG, parm = "POLITY_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_POLITY_lag1_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag2_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY_lag2_noODAG, parm = "POLITY_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_POLITY_lag2_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag3_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY_lag3_noODAG, parm = "POLITY_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_POLITY_lag3_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2_noODAG, parm = "POLITY2_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_POLITY2_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag1_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag1_noODAG, parm = "POLITY2_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_POLITY2_lag1_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag2_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag2_noODAG, parm = "POLITY2_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_POLITY2_lag2_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag3_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag3_noODAG, parm = "POLITY2_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_POLITY2_lag3_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_noODAG, parm = "v2x_LIBDEM_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_v2x_LIBDEM_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag1_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag1_noODAG, parm = "v2x_LIBDEM_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_v2x_LIBDEM_lag1_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag2_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag2_noODAG, parm = "v2x_LIBDEM_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_v2x_LIBDEM_lag2_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag3_noODAG))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = format.pval(`Pr(>|z|)`,digits = 3, eps = 1e-5)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag3_noODAG, parm = "v2x_LIBDEM_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_v2x_LIBDEM_lag3_noODAG)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3, v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "POLITY") ~ "POLITY",
                         str_detect(var, "v2x_LIBDEM") ~ "v2x_LIBDEM"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    n = md("$n$"),
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 3: Full Model (Without ODAG) Parameters for External **Democracy Scores** and Their **Lags**")
  )

```

\newpage

# Appendix

## Full Model Summaries 

The full summaries of the unlagged full and reduced models are shown below for three measures of democracy for a total of 6 models.  In the full models we observe that external countries with larger populations are much more likely to have a connection with the African country.  We also observe African countries are more likely to have connections with external countries when the African country has a larger value of imports from the external country, while the total GNI of the external does not appear to be significant in the presence of these other predictors. When ODAG is included in the model, which keeps only non-African countries as external possibilities, larger values of ODAG are associated with a greater likelihood of an embassy connection.  

```{r}
summary(mod0_TOTLIB1)
summary(mod1_TOTLIB1)
summary(mod1_TOTLIB1_noODAG)

summary(mod0_POLITY)
summary(mod1_POLITY)
summary(mod1_POLITY_noODAG)

summary(mod0_POLITY2)
summary(mod1_POLITY2)
summary(mod1_POLITY2_noODAG)
```

## Random Effect Estimates From the TOTLIB1 Full Model

Large positive values mean that a connection is more likely; Likewise, a large negative number means a connection is less likely.  Notice that as years increase the probability of a connection is more likely the more recent the data indicating more connections are made over time.  The random effects for COUNTRY_INT give the change in the baseline probability of a connection with an external country. Egypt is the largest random effect indicating that the are the most likely to have a connection with an external country when all other factors are held constant. The largest effect for COUNTRY_EXT is the United States, indicating that African countries are most likely to have a connection with the United States with Belgium a close second.  

```{r}
ranef(mod1_TOTLIB1_noODAG)$YEAR
ranef(mod1_TOTLIB1_noODAG)$COUNTRY_INT %>% arrange(-`(Intercept)`)
ranef(mod1_TOTLIB1_noODAG)$COUNTRY_EXT %>% arrange(-`(Intercept)`)
ranef(mod1_TOTLIB1_noODAG)$`COUNTRY_INT:COUNTRY_EXT` %>% arrange(-`(Intercept)`) %>% view()
```
