---
title: "External Report"
author: "Steven Pappas and Gregory J. Matthews"
format: pdf
execute:
  echo: false
  message: false
  warning: false
editor: visual
date: "May 4, 2026"
---

Our external analysis seeks to evaluate the relationship between an external country's democracy score and the likelihood of an embassy in an internal country in a given year. We focused on democracy scores from Freedom House (TOTLIB1) and the POLITY IV database (POLITY and POLITY2).

Our analysis is split into a reduced and full model. The former seeks to evaluate our model relationship without additional external country characteristics. It accounts for random effects in the internal and external countries and their interaction and the year. These random effects shift their respective baseline to better account for differences across groups. For instance, it allows us to better evaluate a baseline for Angola in 2000 instead of assuming it's equivalent to Benin in 1995. 

For the full model, we incorporated the external country's population, GNI, official development assistance gross (ODAG), and trade import gross (TRDIM) in addition to their democracy score and the same random effects. We applied a log transformation to each of these new variables to adjust for their right-skewed distribution. These distribution plots are displayed below in our exploratory data analysis. Finally, we applied this model framework to one to three-year lagged external democracy scores.

# Reduced Model

$$
Y_{ijk} \sim \text{Binomial}(n_{ijk}, p_{ijk})
$$

$$
\text{logit}(p_{ijk}) = \beta_0 + \beta_1X_{1ijk} + \gamma_{0i} + \gamma_{0j} + \gamma_{0ij} + \gamma_{0k} + \epsilon_{ijk}
$$

$$
\gamma_{0i} \sim \text{N}(0, \sigma_i^2)
$$

$$
\gamma_{0j} \sim \text{N}(0, \sigma_j^2)
$$

$$
\gamma_{0ij} \sim \text{N}(0, \sigma_{ij}^2)
$$

$$
\gamma_{0k} \sim \text{N}(0, \sigma_k^2)
$$

Our reduced model equations are written above, where $Y_{ijk}$ is an indicator for an embassy connection between internal country $i$ and external country $j$ in year $k$. In lagged models, the year $k$ changes units depending on the lag. For instance, a one-year lag would produce the model equation $\text{logit}(p_{ijk}) = \beta_0 + \beta_1X_{1ij(k-1)} + \gamma_{0i} + \gamma_{0j} + \gamma_{0ij} + \gamma_{0k} + \epsilon_{ijk}$, where $X_{1ij(k-1)}$ is the external country's democracy score in the prior year (year $k$-1).

As shown in Table 1, all external country democracy scores and their lags show significance at the $\alpha$ = 0.05 level. Interestingly, each model's $\hat{\beta}$ coefficients indicate that the less democratic external country $j$ the more likely they are to have an embassy relationship with internal country $i$. For instance, a one-unit increase in unlagged TOTLIB1 (where a higher score indicates a less democratic country) increases the odds of an embassy relationship by a factor of 1.203.

# Full Model

$$
Y_{ijk} \sim \text{Binomial}(n_{ijk}, p_{ijk})
$$

$$
\text{logit}(p_{ijk}) = \beta_0 + \beta_1X_{1ijk} + \ldots + \beta_4X_{4ijk} + \gamma_{0i} + \gamma_{0j} + \gamma_{0ij} + \gamma_{0k} + \epsilon_{ijk}
$$

$$
\gamma_{0i} \sim \text{N}(0, \sigma_i^2)
$$

$$
\gamma_{0j} \sim \text{N}(0, \sigma_j^2)
$$

$$
\gamma_{0ij} \sim \text{N}(0, \sigma_{ij}^2)
$$

$$
\gamma_{0k} \sim \text{N}(0, \sigma_k^2)
$$

Our full model equations largely follow the same setup as the reduced model with the addition of the aforementioned log-transformed external country characteristics.

As shown in Table 2, the only significant variable at the $\alpha$ = 0.05 level is the two-year lagged TOTLIB1 score. Additionally, the democracy score's effect sizes, as shown by their $\hat{\beta}$ coefficients, are much smaller than their reduced model counterparts. For instance, a one-unit increase in the two-year lagged TOTLIB1 score decreases the odds of an embassy relationship by a factor of 0.983, or a 1.7 percent decrease. Interestingly, this relationship is the reverse of its reduced model counterpart. However, given the small effect size, it is better to conclude the relationship is minimal rather than opposite the reduced model.

```{r}

library(tidyverse)
library(readxl)
library(data.table)

masterset = read_csv("data/Master 08-28-2025 AFP excel dataset-3.xlsx - AFRSdata.csv")

restofworld = read_excel("data/Rest of the World.xlsx")

masterset = masterset %>%
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         across(where(is.numeric), ~ na_if(., -88)),
         across(where(is.numeric), ~ na_if(., -77)),
         across(where(is.numeric), ~ na_if(., -66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY))

masterset$GNI <- gsub(",",".",masterset$GNI)
masterset$GNI <- gsub(" ","",masterset$GNI)%>% as.numeric()

masterset$GNI_CAP <- gsub(",",".",masterset$GNI_CAP)
masterset$GNI_CAP <- gsub(" ","",masterset$GNI_CAP)%>% as.numeric()

masterset$POPULATN <- gsub(",",".",masterset$POPULATN)
masterset$POPULATN <- gsub(" ","",masterset$POPULATN) %>% as.numeric()

names(masterset)[which(names(masterset) == "TRDX352b")] <- "TRDEX352b"
names(masterset)[which(names(masterset) == "TRDX200h")] <- "TRDEX200h"
names(masterset)[which(names(masterset) == "TRDX200m")] <- "TRDEX200m"
names(masterset)[which(names(masterset) == "TDX321sr")] <- "TRDEX321sr"
names(masterset)[which(names(masterset) == "TDX321sm")] <- "TRDEX321sm"
names(masterset)[which(names(masterset) == "TDX321yr")] <- "TRDEX321yr"

names(masterset)[which(names(masterset) == "TRDI200h")] <- "TRDIM200h"
names(masterset)[which(names(masterset) == "TRDI200m")] <- "TRDIM200m"
names(masterset)[which(names(masterset) == "TDI321sr")] <- "TRDIM321sr"
names(masterset)[which(names(masterset) == "TDI321sm")] <- "TRDIM321sm"
names(masterset)[which(names(masterset) == "TDI321yr")] <- "TRDIM321yr"
names(masterset)[which(names(masterset) == "TDI316SU")] <- "TRDIM316su"

restofworld <- restofworld %>% 
  mutate(GNI = as.numeric(GNI),
         GNI_CAP = as.numeric(GNI_CAP),
         AVLIFEEX = as.numeric(AVLIFEEX),
         ENRGUSE = as.numeric(ENRGUSE)) %>% 
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         across(where(is.numeric), ~ na_if(., -88)),
         across(where(is.numeric), ~ na_if(., -77)),
         across(where(is.numeric), ~ na_if(., -66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY))

restofworld$GNI <- gsub(",",".",restofworld$GNI)
restofworld$GNI <- gsub(" ","",restofworld$GNI)%>% as.numeric()

restofworld$GNI_CAP <- gsub(",",".",restofworld$GNI_CAP)
restofworld$GNI_CAP <- gsub(" ","",restofworld$GNI_CAP)%>% as.numeric()

restofworld$POPULATN <- gsub(",",".",restofworld$POPULATN)
restofworld$POPULATN <- gsub(" ","",restofworld$POPULATN) %>% as.numeric()

countrycodes <- list(
  world = restofworld %>%
    select(CCODE:COUNTRY) %>%
    unique(),
  africa = masterset %>%
    select(CCODE:COUNTRY) %>%
    mutate(CCODE = paste0("C", CCODE)) %>%
    unique()
) %>%
  rbindlist()

external_democracy <- list(
  world = restofworld %>%
    select(CCODE,YEAR,TOTLIB1, POLITY, POLITY2,GNI, GNI_CAP, POPULATN) %>%
    unique(),
  africa = masterset %>%
    select(CCODE,YEAR,TOTLIB1, POLITY, POLITY2,GNI, GNI_CAP, POPULATN) %>%
    mutate(CCODE = paste0("C", CCODE)) %>%
    unique()
) %>%
  rbindlist()

countrycodes <- countrycodes %>% 
  mutate(CCODE = ifelse(CCODE == "C99","C099",CCODE))

external_democracy <- external_democracy %>% 
  mutate(CCODE = ifelse(CCODE == "C99","C099",CCODE)) %>%
  rename_with(
    .fn = ~ paste0(.x, "_EXT"),
    .cols = -YEAR
  ) %>%
  arrange(CCODE_EXT, YEAR) %>% 
  group_by(CCODE_EXT)  %>% 
  mutate(TOTLIB1_EXT_lag1 = lag(TOTLIB1_EXT,1),
         TOTLIB1_EXT_lag2 = lag(TOTLIB1_EXT,2),
         TOTLIB1_EXT_lag3 = lag(TOTLIB1_EXT,3),
         POLITY_EXT_lag1 = lag(POLITY_EXT,1),
         POLITY_EXT_lag2 = lag(POLITY_EXT,2),
         POLITY_EXT_lag3 = lag(POLITY_EXT,3),
         POLITY2_EXT_lag1 = lag(POLITY2_EXT,1),
         POLITY2_EXT_lag2 = lag(POLITY2_EXT,2),
         POLITY2_EXT_lag3 = lag(POLITY2_EXT,3)
  ) %>% 
  ungroup()

newdata <- masterset %>%
  select(CCODE_INT = CCODE, COUNTRY_INT = COUNTRY, YEAR, C099:C572) %>%
  mutate(CCODE_INT = paste0("C", CCODE_INT)) %>%
  pivot_longer(!CCODE_INT:YEAR, names_to = "CCODE_EXT", values_to = "CONNECTION") %>%
  left_join(countrycodes, by = c("CCODE_EXT" = "CCODE"), relationship = "many-to-many") %>%
  select(CONNECTION, CCODE_INT, COUNTRY_INT, CCODE_EXT, COUNTRY_EXT = COUNTRY, 
         everything()) %>%
  filter(CONNECTION %in% c(0, 1), CCODE_INT != CCODE_EXT) %>% 
  left_join(external_democracy, by = c("CCODE_EXT","YEAR" = "YEAR")) %>%
  mutate(GNI_EXT = as.numeric(GNI_EXT),
         GNI_CAP_EXT = as.numeric(GNI_CAP_EXT))

odag_data <- masterset %>% rename(ODAG251 = odag251) %>% 
  select(CCODE_INT = CCODE, COUNTRY_INT = COUNTRY, YEAR, ODAG201:ODAG643, ODAG251) %>% 
  mutate(across(c(ODAG201:ODAG643,ODAG251), ~ gsub(",", ".", .x))) %>% 
  mutate(across(c(ODAG201:ODAG643,ODAG251), as.numeric)) %>% 
  pivot_longer(cols = c(ODAG201:ODAG643,ODAG251), names_to ="CCODE_EXT", values_to = "ODAG") %>% 
  mutate(CCODE_EXT = gsub( "ODAG","",CCODE_EXT)) %>%
  mutate(CCODE_EXT = paste0("C", CCODE_EXT),
         CCODE_INT = paste0("C", CCODE_INT)) %>% 
  filter(CCODE_INT != "CNA" & ODAG != -99)

trdex_data <- masterset %>% 
  select(CCODE_INT = CCODE, 
         COUNTRY_INT = COUNTRY, 
         YEAR, 
         matches("^TRDEX\\d{3}")) %>% 
  mutate(across(TRDEX351:TRDEX203, ~ gsub(",", ".", .x))) %>% 
  mutate(across(TRDEX351:TRDEX203, as.numeric)) %>% 
  mutate(TRDEX200 = ifelse((is.na(TRDEX200) &
                              is.na(TRDEX200h) &
                              is.na(TRDEX200h)),
                           NA,
                           rowSums(across(c(TRDEX200, TRDEX200h, TRDEX200m)), na.rm = TRUE)
  )) %>%
  mutate(TRDEX321 = ifelse((is.na(TRDEX321sm) &
                              is.na(TRDEX321sr) &
                              is.na(TRDEX321yr)),
                           NA,
                           rowSums(across(c(TRDEX321sm, TRDEX321sr, TRDEX321yr)), na.rm = TRUE)
  )) %>% #combining 321 yr, sm, se
  pivot_longer(cols = TRDEX351:TRDEX321, names_to ="CCODE_EXT", values_to = "TRDEX") %>%
  mutate(CCODE_EXT = gsub( "TRDEX","",CCODE_EXT)) %>% 
  mutate(CCODE_EXT = paste0("C", CCODE_EXT),
         CCODE_INT = paste0("C", CCODE_INT)) %>% 
  filter(CCODE_INT != "CNA")

trdim_data <- masterset %>% 
  select(CCODE_INT = CCODE, 
         COUNTRY_INT = COUNTRY, 
         YEAR, 
         matches("^TRDIM\\d{3}")) %>% 
  mutate(across(TRDIM351:TRDIM203, ~ gsub(",", ".", .x))) %>% 
  mutate(across(TRDIM351:TRDIM203, as.numeric)) %>% 
  mutate(TRDIM200 = ifelse((is.na(TRDIM200) &
                              is.na(TRDIM200h) &
                              is.na(TRDIM200h)),
                           NA,
                           rowSums(across(c(TRDIM200, TRDIM200h, TRDIM200m)), na.rm = TRUE)
  )) %>% #summing 200, 200m, 200h to combine China
  mutate(TRDIM321 = ifelse((is.na(TRDIM321sm) &
                              is.na(TRDIM321sr) &
                              is.na(TRDIM321yr)),
                           NA,
                           rowSums(across(c(TRDIM321sm, TRDIM321sr, TRDIM321yr)), na.rm = TRUE)
  )) %>% #combining 321 yr, sm, se
  mutate(TRDIM316 = ifelse((is.na(TRDIM316) &
                              is.na(TRDIM316su)),
                           NA,
                           rowSums(across(c(TRDIM316,TRDIM316su)), na.rm = TRUE)
  )) %>% #combining 316 and 316su (i.e. Russia and Soviet Union)
  pivot_longer(cols = TRDIM351:TRDIM321, names_to ="CCODE_EXT", values_to = "TRDIM") %>% 
  mutate(CCODE_EXT = gsub( "TRDIM","",CCODE_EXT)) %>%
  mutate(CCODE_EXT = paste0("C", CCODE_EXT),
         CCODE_INT = paste0("C", CCODE_INT)) %>% 
  filter(CCODE_INT != "CNA") %>% filter(!(CCODE_INT == "C114" & CCODE_EXT == "C148" & YEAR == 1972))

cleandata <- newdata %>% 
  left_join(odag_data %>% select(CCODE_INT,YEAR,CCODE_EXT,ODAG), 
            by = c("CCODE_INT","CCODE_EXT","YEAR")) %>%
  left_join(trdex_data %>% select(CCODE_INT,YEAR,CCODE_EXT,TRDEX), 
            by = c("CCODE_INT","CCODE_EXT","YEAR")) %>%
  left_join(trdim_data %>% select(CCODE_INT,YEAR,CCODE_EXT,TRDIM), 
            by = c("CCODE_INT","CCODE_EXT","YEAR")) %>% 
  mutate(logGNI_EXT = log(GNI_EXT, 10),
         logPOP_EXT = log(POPULATN_EXT, 10),
         logODAG = log(ODAG+1,10),
         logTRDIM = log(TRDIM+1,10),
         logTRDEX = log(TRDEX+1,10),
         ODAG = ifelse(ODAG == -99, NA, ODAG),
         TRDIM = ifelse(TRDIM == -99, NA, TRDIM)) %>% 
  filter(ODAG >= 0) %>% ungroup()

```

```{r}

cleandata %>% 
  ggplot(aes(x = POPULATN_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Population Density of External Countries",
    x = "External Country Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>% 
  ggplot(aes(x = logPOP_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Population Density of External Countries",
    x = "Log-Transformed External Country Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>% 
  ggplot(aes(x = GNI_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Gross National Income (GNI) Density of External Countries",
    x = "External Country GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>% 
  ggplot(aes(x = logGNI_EXT)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Gross National Income (GNI) Density of External Countries",
    x = "Log-Transformed External Country GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>% 
  ggplot(aes(x = ODAG)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Official Development Assistance Gross (ODAG) Density of External Countries",
    x = "External Country ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>% 
  ggplot(aes(x = logODAG)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Official Development Assistance Gross (ODAG) Density of External Countries",
    x = "Log-Transformed External Country ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>% 
  ggplot(aes(x = TRDIM)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Total Import (TRDIM) Density of External Countries",
    x = "External Country TRDIM"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>% 
  ggplot(aes(x = logTRDIM)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Total Import (TRDIM) Density of External Countries",
    x = "Log-Transformed External Country TRDIM"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

```

```{r}

interaction <- cleandata %>%
  group_by(CCODE_INT, COUNTRY_INT, CCODE_EXT, COUNTRY_EXT) %>%
  reframe(N = n())

interaction2 <- list(
  world = restofworld %>%
    select(CCODE_EXT = CCODE, COUNTRY_EXT = COUNTRY) %>%
    unique(),
  africa = masterset %>%
    mutate(CCODE_INT = paste0("C", CCODE)) %>%
    select(CCODE_INT, COUNTRY_INT = COUNTRY) %>%
    unique()
) %>%
  reduce(merge, by = NULL) %>%
  left_join(interaction, by = c("CCODE_INT", "COUNTRY_INT", "CCODE_EXT", "COUNTRY_EXT")) %>%
  mutate(N = ifelse(is.na(N), 0, N))

table(interaction2$N)

round(table(interaction2$N)/nrow(interaction2)*100, 1)

```

```{r}

cleandata %>%
  mutate(CONNECTION = as.factor(CONNECTION)) %>%
  ggplot(aes(x = CONNECTION, y = TOTLIB1_EXT)) +
  geom_boxplot() +
  scale_y_continuous(limits = c(0, 15)) +
  facet_wrap(~YEAR) +
  labs(
    title = "Boxplot of External Country TOTLIB1 by External-Internal Country Connection and Year",
    x = "External-Internal Country Connection",
    y = "External Country TOTLIB1"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>%
  mutate(CONNECTION = as.factor(CONNECTION)) %>%
  ggplot(aes(x = CONNECTION, y = POLITY_EXT)) +
  geom_boxplot() +
  scale_y_continuous(limits = c(-10, 10)) +
  facet_wrap(~YEAR) +
  labs(
    title = "Boxplot of External Country POLITY by External-Internal Country Connection and Year",
    x = "External-Internal Country Connection",
    y = "External Country POLITY"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

cleandata %>%
  mutate(CONNECTION = as.factor(CONNECTION)) %>%
  ggplot(aes(x = CONNECTION, y = POLITY2_EXT)) +
  geom_boxplot() +
  scale_y_continuous(limits = c(0, 15)) +
  facet_wrap(~YEAR) +
  labs(
    title = "Boxplot of External Country POLITY2 by External-Internal Country Connection and Year",
    x = "External-Internal Country Connection",
    y = "External Country POLITY2"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

```

```{r}

cordata <- cleandata %>%
  select(logPOP_EXT, logGNI_EXT, logODAG, logTRDIM, YEAR) %>%
  drop_na()

cat("Pearson Correlation")

cor(cordata, method = "pearson")

cat("Kendall-Tau Correlation")

cor(cordata, method = "kendall")

cat("Spearman Correlation")

cor(cordata, method = "spearman")

```

```{r}

library(lme4)

load("~/PeterSchraeder/externalmodels/mod0_TOTLIB1.RData")

load("externalmodels/mod0_TOTLIB1_lag1.RData")

load("externalmodels/mod0_TOTLIB1_lag2.RData")

load("externalmodels/mod0_TOTLIB1_lag3.Rdata")

load("externalmodels/mod0_POLITY.Rdata")

load("externalmodels/mod0_POLITY_lag1.Rdata")

load("externalmodels/mod0_POLITY_lag2.Rdata")

load("externalmodels/mod0_POLITY_lag3.Rdata")

load("externalmodels/mod0_POLITY2.Rdata")

load("externalmodels/mod0_POLITY2_lag1.Rdata")

load("externalmodels/mod0_POLITY2_lag2.Rdata")

load("externalmodels/mod0_POLITY2_lag3.Rdata")

```

```{r}

library(gt)

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_TOTLIB1, parm = "TOTLIB1_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod0_TOTLIB1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_TOTLIB1_lag1, parm = "TOTLIB1_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod0_TOTLIB1_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_TOTLIB1_lag2, parm = "TOTLIB1_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod0_TOTLIB1_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_TOTLIB1_lag3, parm = "TOTLIB1_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod0_TOTLIB1_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY, parm = "POLITY_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod0_POLITY)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY_lag1, parm = "POLITY_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod0_POLITY_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY_lag2, parm = "POLITY_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod0_POLITY_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY_lag3, parm = "POLITY_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod0_POLITY_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY2, parm = "POLITY2_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod0_POLITY2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY2_lag1, parm = "POLITY2_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod0_POLITY2_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY2_lag2, parm = "POLITY2_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod0_POLITY2_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_POLITY2_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod0_POLITY2_lag3, parm = "POLITY2_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod0_POLITY2_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "POLITY") ~ "POLITY"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    n = md("$n$"),
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 1: Reduced Model Parameters for External **Democracy Scores** and Their **Lags**")
  )

```

```{r}

load("externalmodels/mod1_TOTLIB1.Rdata")

load("externalmodels/mod1_TOTLIB1_lag1.Rdata")

load("externalmodels/mod1_TOTLIB1_lag2.Rdata")

load("externalmodels/mod1_TOTLIB1_lag3.Rdata")

load("externalmodels/mod1_POLITY.Rdata")

load("externalmodels/mod1_POLITY_lag1.Rdata")

load("externalmodels/mod1_POLITY_lag2.Rdata")

load("externalmodels/mod1_POLITY_lag3.Rdata")

load("externalmodels/mod1_POLITY2.Rdata")

load("externalmodels/mod1_POLITY2_lag1.Rdata")

load("externalmodels/mod1_POLITY2_lag2.Rdata")

load("externalmodels/mod1_POLITY2_lag3.Rdata")

```

```{r}

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1, parm = "TOTLIB1_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_TOTLIB1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag1, parm = "TOTLIB1_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_TOTLIB1_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag2, parm = "TOTLIB1_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_TOTLIB1_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag3, parm = "TOTLIB1_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_TOTLIB1_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY, parm = "POLITY_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_POLITY)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY_lag1, parm = "POLITY_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_POLITY_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY_lag2, parm = "POLITY_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_POLITY_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY_lag3, parm = "POLITY_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_POLITY_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2, parm = "POLITY2_EXT", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0", n = nobs(mod1_POLITY2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag1") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag1, parm = "POLITY2_EXT_lag1", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1", n = nobs(mod1_POLITY2_lag1)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag2") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag2, parm = "POLITY2_EXT_lag2", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2", n = nobs(mod1_POLITY2_lag2)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_POLITY2_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_EXT_lag3") %>%
    mutate(Estimate_exp = exp(Estimate), Estimate = round(Estimate, 3), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag3, parm = "POLITY2_EXT_lag3", level = 0.95, method = "Wald")) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3", n = nobs(mod1_POLITY2_lag3)) %>%
  select(var, lag, n, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "POLITY") ~ "POLITY"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    n = md("$n$"),
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 2: Full Model Parameters for External **Democracy Scores** and Their **Lags**")
  )

```

```{r}

summary(mod0_TOTLIB1)
summary(mod1_TOTLIB1)

summary(mod0_POLITY)
summary(mod1_POLITY)

summary(mod0_POLITY2)
summary(mod1_POLITY2)

```
