---
title: "HHI Report"
author: "Gregory J. Matthews and Steven Pappas"
format: pdf
execute:
  echo: false
  message: false
  warning: false
editor: visual
date: "August 31, 2026"
---



<!-- NOTE: for Totlib1 lower scores are MORE democracy -->

<!-- summary(mod1_v2x_LIBDEM_lag1) -->

<!-- v2x_Libdem lag 1 didn't converge -->

This analysis seeks to evaluate the relationship between a country's Herfindahl-Hirschman Index (HHI) and their democracy score. The HHI uses a country's official development assistance gross (ODAG) share from external countries. We used democracy scores from Freedom House (TOTLIB1), the POLITY IV database (POLITY and POLITY2), and the Liberal Democracy Index from the V-Dem Institute (v2x_libdem).

This main analyses were split into two parts: a reduced model and a full model. The reduced model only considers democracy as a fixed effect, while including random intercepts for the internal country, the external country, their interaction, and the year. These random effects account for correlation between observations with in the structure of the data.

The full model includes all of the parts of the reduced model, but also includes the external country's population, GNI, ODAG (Note: When ODAG is not observed it is set to 0 in the analysis), and total sum of trade import and export gross (TRDTOT). We applied a log transformation to each of these predictor variables due to their fairly extreme right-skewness (shown in the following density plots). We applied both of these model with lagged democracy scores of 1, 2, and 3 years. Finally, note that the POLITY model was dropped here as there were convergence issues in parameter estimation with the addition of TRDTOT and ODAG with a large number of zeroes. These convergence issues were not present when using POLITY2.

# Reduced Model

The reduced model equations are given below, where the response $Y_{it}$ ranges from 1/$k$ to 1 for African country $i$ in year $t$ and $k$ is the number of possible sources of ODAG. We applied a log transformation to HHI to fix its heavy non-constant variance, where the residuals increased in size as the fitted values increased. The predictor $X_{1it}$ represents the democracy score of African country $i$ in year $t$.

In lagged models, the year $t$ changes units depending on the lag. For instance, a one-year lag would produce the model equation $\text{log}(HHI_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$, where $X_{1i(t-1)}$ is the external country's democracy score in the prior year (year $t$-1).

$$Y_{it} \sim \text{N}(\mu_{it}, \sigma^2)$$

$\text{log}(HHI_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$

$$\gamma_{0i} \sim \text{N}(0, \sigma_{country}^2)$$

$$\gamma_{0t} \sim \text{N}(0, \sigma_{year}^2)$$



# Full Model

Our full model equations are given below. They largely follow the same setup as the reduced model with the addition of the aforementioned log-transformed country characteristics. In lagged models, we only lagged the country's democracy score. For instance, a one-year lag would produce the model equation $\text{log}(HHI_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \ldots + \beta_5X_{5it} + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$, where $X_{1i(t-1)}$ is the country's democracy score in the prior year (year $t$-1).

$$Y_{it} \sim \text{N}(\mu_{it}, \sigma^2)$$

$$\text{log}(HHI_{it}) = \beta_0 + \beta_1X_{1ik} + \ldots + \beta_5X_{5it} + \gamma_{0i} + \gamma_{tk} + \epsilon_{it}$$

$$\gamma_{0i} \sim \text{N}(0, \sigma_{country}^2)$$

$$\gamma_{0t} \sim \text{N}(0, \sigma_{year}^2)$$

<!-- We gotta fix this.  This isn't significant.  The model didn't converge.  You can tell this because the confidence interval is so narrow it's ridiculous and very different from the others.  -->

<!-- As shown in Table 2, none of the democracy scores are significant at the $\alpha$ = 0.05 level. External population size, the amount of aid sent to an internal country (ODAG), and imports (TRDIM) are all highly significant and all show a positive relationship with the probability of a connection.   -->


```{r}
#Note original Hirschman ideas was the sqaure root of the sum of squres of market share. 
#HHI is now just the sum of squares.  
library(tidyverse)
library(readxl)

setwd("/Users/gregorymatthews/Dropbox/african_foreign_policy_git/")

#masterset = read_csv("data/Master 08-28-2025 AFP excel dataset-3.csv")
masterset = read_csv("data2026/MASTER DATASET 3.26.2026.csv")

#restofworldold = read_excel("data/Rest of the World.xlsx")
#restofworld = read_excel("data2026/Rest of the World - 5.6.2026.xlsx")


## Cleaning data ##
masterset = masterset %>%
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         across(where(is.numeric), ~ na_if(., -88)),
         across(where(is.numeric), ~ na_if(., -77)),
         across(where(is.numeric), ~ na_if(., -66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY))

#Convert commas to periods. 
#it looks like commas are being used as the decimal.  
#Fix the nonsense formatting from excel. 
masterset$GNI <- gsub(",",".",masterset$GNI)
masterset$GNI <- gsub(" ","",masterset$GNI)%>% as.numeric()

masterset$GNI_CAP <- gsub(",",".",masterset$GNI_CAP)
masterset$GNI_CAP <- gsub(" ","",masterset$GNI_CAP)%>% as.numeric()

masterset$POPULATN <- gsub(",",".",masterset$POPULATN)
masterset$POPULATN <- gsub(" ","",masterset$POPULATN) %>% as.numeric()

#Manually fixing names
names(masterset)[which(names(masterset) == "TRDX352b")] <- "TRDEX352b" #These years are getting dropped.  
names(masterset)[which(names(masterset) == "TRDX200h")] <- "TRDEX200h"
names(masterset)[which(names(masterset) == "TRDX200m")] <- "TRDEX200m"
names(masterset)[which(names(masterset) == "TDX321sr")] <- "TRDEX321sr"
names(masterset)[which(names(masterset) == "TDX321sm")] <- "TRDEX321sm"
names(masterset)[which(names(masterset) == "TDX321yr")] <- "TRDEX321yr"

names(masterset)[which(names(masterset) == "TRDI200h")] <- "TRDIM200h"
names(masterset)[which(names(masterset) == "TRDI200m")] <- "TRDIM200m"
names(masterset)[which(names(masterset) == "TDI321sr")] <- "TRDIM321sr"
names(masterset)[which(names(masterset) == "TDI321sm")] <- "TRDIM321sm"
names(masterset)[which(names(masterset) == "TDI321yr")] <- "TRDIM321yr"
names(masterset)[which(names(masterset) == "TDI316SU")] <- "TRDIM316su"

masterset <- masterset %>% mutate(ODAG404 = as.numeric(ODAG404))

HHI <- masterset %>%
  mutate(across(ODAG201:ODAG501, ~ replace_na(.x, 0))) %>% #replace NA with 0
  mutate(across(ODAG201:ODAG501, ~ pmax(.x, 0))) %>% #no negative numbers
  mutate(across(ODAG201:ODAG501, ~ as.numeric(.x))) %>% #make these variables numeric
  rowwise() %>% 
  mutate(ODAGTOT200_501 = rowSums(across(ODAG201:ODAG501))) %>% 
  mutate(HHI = rowSums((across(ODAG201:ODAG501) / rowSums(across(ODAG201:ODAG501)))^2)) %>% 
  mutate(HHI = ifelse(ODAGTOT200_501 == 0, NA, HHI))


#HHI values over time
#HHI %>% select(COUNTRY, YEAR, HHI, ODAGTOT200_500, ODAG201:ODAG416) %>% write.csv(file = "./HHI.csv", row.names = FALSE)

HHI %>% ggplot(aes(x = YEAR, y = HHI)) + geom_line() +  facet_wrap(~COUNTRY) + theme_bw()


## Prepare data for analysis. 
HHI <- HHI %>% mutate(across(TRDEX351:TRDEX203, ~ as.numeric(.x))) %>% 
  mutate(across(TRDIM351:TRDIM203, ~ as.numeric(.x))) %>% 
  mutate(TRDEXtot = rowSums(pick(TRDEX351:TRDEX250, 
                                 TRDEX300:TRDEX285, 
                                 TRDEX280:TRDEX415,
                                 TRDEX100:TRDEX147,
                                 TRDEX577:TRDEX551,
                                 TRDEX563:TRDEX203),na.rm = TRUE),
         TRDIMtot = rowSums(pick(TRDIM351:TRDIM250,
                                 TRDIM300:TRDIM285,
                                 TRDIM280:TRDIM415,
                                 TRDIM100:TRDIM147,
                                 TRDIM577:TRDIM551,
                                 TRDIM563:TRDIM203),na.rm = TRUE)) %>% 
  mutate(ODAGtot = rowSums(pick(ODAG201:ODAG501), na.rm = T)) %>% 
  mutate(POPULATN = ifelse(POPULATN == -99, NA, POPULATN),
         logGNI = log(GNI, 10),
         logPOP = log(POPULATN,10),
         logTRDIMtot = log(TRDIMtot + 1,10),
         logTRDEXtot = log(TRDEXtot + 1,10), 
         logODAGtot = log(ODAGtot + 1, 10)) 

#Now create the lag variables
HHI <- HHI %>% arrange(CCODE, YEAR) %>% group_by(CCODE) %>% 
  mutate(TOTLIB1_lag1 = lag(TOTLIB1,1),
         TOTLIB1_lag2 = lag(TOTLIB1,2),
         TOTLIB1_lag3 = lag(TOTLIB1,3),
         POLITY_lag1 = lag(POLITY,1),
         POLITY_lag2 = lag(POLITY,2),
         POLITY_lag3 = lag(POLITY,3),
         POLITY2_lag1 = lag(POLITY2,1),
         POLITY2_lag2 = lag(POLITY2,2),
         POLITY2_lag3 = lag(POLITY2,3)
  ) %>% 
  ungroup() %>% mutate(logitHHI = log(ifelse(HHI == 1,0.999,HHI)/(1-ifelse(HHI == 1,0.999,HHI))))
  
```

```{r echo = FALSE}
#Summary stuff
HHI %>% filter(YEAR >= 1960) %>%group_by(YEAR) %>% summarize(meanHHI = mean(HHI, na.rm = T)) 
HHI %>% filter(YEAR >= 1960) %>%group_by(YEAR) %>% summarize(meanHHI = mean(HHI, na.rm = T))  %>% ggplot(aes(x = YEAR, y = meanHHI)) + geom_point() + geom_line() + theme_bw()
HHI %>% ggplot(aes(x = YEAR, y = log(HHI))) + geom_point() + geom_smooth(se = F)  + theme_bw()
HHI %>% ggplot(aes(x = HHI)) + geom_density() + theme_bw()


#
HHI %>% ggplot(aes(x = POLITY2, y = log(HHI), color = YEAR, group = YEAR)) + geom_point() + geom_smooth(se = F)  + theme_bw()
HHI %>% ggplot(aes(x = POLITY, y = log(HHI), color = YEAR, group = YEAR)) + geom_point() + geom_smooth(se = F)  + theme_bw()
HHI %>% ggplot(aes(x = TOTLIB1, y = log(HHI), color = YEAR, group = YEAR)) + geom_point() + geom_smooth(se = F)  + theme_bw()
HHI %>% ggplot(aes(x = logODAGtot, y = (HHI))) + geom_point() + geom_smooth(se = F)  + theme_bw()
HHI %>% ggplot(aes(x = logGNI, y = (HHI))) + geom_point() + geom_smooth(se = F)  + theme_bw()
HHI %>% ggplot(aes(x = logPOP, y = (HHI))) + geom_point() + geom_smooth(se = F)  + theme_bw()
```

```{r eval = FALSE}
#Build some models
#HHI = 1 if there is a monopoly
#Smaller HHI 
library(lme4)
library(lmerTest)
library(splines)
mod0_POLITY2 <- lmer(log(HHI) ~ POLITY2  + (1|CCODE) + (1|YEAR), data = HHI)
mod1_POLITY2 <- lmer(log(HHI) ~  POLITY2  + logPOP + I(logPOP^2) + I(logPOP^3) + logGNI + I(logGNI^2)  + logODAGtot + I(logODAGtot^2) + (1|CCODE) + (1|YEAR) , data = HHI)

mod0_POLITY <- lmer(log(HHI) ~ POLITY  + (1|CCODE) + (1|YEAR), data = HHI)
mod1_POLITY <- lmer(log(HHI) ~  POLITY  + logPOP + I(logPOP^2) + I(logPOP^3) + logGNI + I(logGNI^2)  + logODAGtot + I(logODAGtot^2) + (1|CCODE) + (1|YEAR) , data = HHI)

mod0_TOTLIB1 <- lmer(log(HHI) ~ TOTLIB1  + (1|CCODE) + (1|YEAR), data = HHI)
mod1_TOTLIB1 <- lmer(log(HHI) ~  TOTLIB1 + logPOP + I(logPOP^2) + I(logPOP^3) + logGNI  + I(logGNI^2) + logODAGtot + I(logODAGtot^2) + (1|CCODE) + (1|YEAR) , data = HHI)

```

```{r echo = FALSE}
load("./HHImodels/mod0_POLITY2.RData")
load("./HHImodels/mod1_POLITY2.RData")

load("./HHImodels/mod0_POLITY.RData")
load("./HHImodels/mod1_POLITY.RData")

load("./HHImodels/mod0_TOTLIB1.RData")
load("./HHImodels/mod1_TOTLIB1.RData")
```

```{r}
summary(mod0_POLITY2)
summary(mod1_POLITY2)

summary(mod0_POLITY)
summary(mod1_POLITY)

summary(mod0_TOTLIB1)
summary(mod1_TOTLIB1)
```

