---
title: "ODAG Report"
author: "Gregory J. Matthews and Steven Pappas"
format: pdf
execute:
  echo: false
  message: false
  warning: false
editor: visual
date: "September 28, 2026"
---

# Overview

This analysis seeks to evaluate the relationship between an African country's official development assistance gross (ODAG) and their democracy score. ODAG measures the aid received by an African country from external countries and private organizations. We used democracy scores from Freedom House (TOTLIB1), the POLITY IV database (POLITY2), and the Liberal Democracy Index from the V-Dem Institute (V2x_Libdem). (Note: Here we only analyze POLITY2, whereas in previous reports we have analyzed both POLITY and POLITY2.)

This main analyses were split into a reduced and full model. The reduced model only considers democracy as a fixed effect, while including random intercepts for the African country and year. These random effects account for structural correlation between observations within the data structure.

The full model includes all of the parts of the reduced model while adding the African country's population, gross national income (GNI), and total ODAG (Note: When ODAG is not observed it is set to 0 in the analysis). We applied a log transformation to each of these predictor variables due to their right skew and quadratic or cubic transformations when necessary to capture nonlinear relationships.

In the reduced models, every V2x_Libdem and POLITY2 coefficient is significant at $\alpha$ = 0.05. The negative direction of their coefficients indicate that, as an African country is more democratic, their HHI drops on average meaning that they tend to have more external countries providing development aid and vice versa.  Results for the significance of democracy variables in the reduced model are displayed in Table 1. 

In the full models, every democracy score coefficient except POLITY2 in the lag0 and lag1 models is significant at $\alpha$ = 0.05. The negative direction of the V2x_Libdem and POLITY2 coefficients and positive direction of the TOTLIB1 coefficients provide the same conclusion as the the reduced models. That is, controlling for population, total ODAG, GNI, as an African country is more democratic, it tends to have lower HHI scores on average indicating a greater diversity of countries providing development aid and vice versa.  Results for the significance of democracy variables in the reduced model are displayed in Table 2.  Full model results for all variables in the full models along with random effects estimates are presented for all models in the appendix.   

# Models 

## Reduced Model

The reduced model is described below, where the response $Y_{it}$ is ODAG for African country $i$ in year $t$. We applied a log transformation to ODAG for better model fit. The predictor $X_{1it}$ represents the democracy score of African country $i$ in year $t$.

In lagged models, the year $t$ changes units depending on the lag. For instance, a one-year lag would produce the model equation $\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$, where $X_{1i(t-1)}$ is the external country's democracy score in the prior year (year $t$-1).

$$Y_{it} \sim \text{N}(\mu_{it}, \sigma^2)$$

$\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$

$$\gamma_{0i} \sim \text{N}(0, \sigma_{\text{country}}^2)$$

$$\gamma_{0t} \sim \text{N}(0, \sigma_{\text{year}}^2)$$

# Full Model

Our full model equations are given below. They follow the same setup as the reduced model with the addition of the aforementioned transformed country characteristics. In lagged models, we only lagged the country's democracy score. For instance, a one-year lag would produce the model equation $\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \ldots  + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$, where $X_{1i(t-1)}$ is the country's democracy score in the prior year (year $t$-1).

Additional predictors in this model include the African country's log-transformed GNI, population, and total ODAG. Quadratic terms were included for the log-transformed GNI, population, and total ODAG. The log-transformed population variable added a cubic term to capture further nonlinear tendencies.

$$Y_{it} \sim \text{N}(\mu_{it}, \sigma^2)$$

$$\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1ik} + \ldots + \gamma_{0i} + \gamma_{tk} + \epsilon_{it}$$

$$\gamma_{0i} \sim \text{N}(0, \sigma_{\text{country}}^2)$$

$$\gamma_{0t} \sim \text{N}(0, \sigma_{\text{year}}^2)$$

# Data Visualizations and Results

```{r}

library(tidyverse)
library(readxl)

## Cleaning data ##

masterset = read_csv("./data2026/MASTER DATASET - 9.10.2026.csv")

masterset = masterset %>%
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         across(where(is.numeric), ~ na_if(., -88)),
         across(where(is.numeric), ~ na_if(., -77)),
         across(where(is.numeric), ~ na_if(., -66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY),
         COLD_WAR = ifelse(YEAR >= 1992, 0, 1), 
         COLPAST1 = as.factor(COLPAST1),
         REGION = as.factor(REGION))

# Convert commas to periods. 
# It looks like commas are being used as the decimal.  
# Fix the nonsense formatting from excel. 

masterset$GNI <- gsub(",",".",masterset$GNI)
masterset$GNI <- gsub(" ","",masterset$GNI)%>% as.numeric()

masterset$GNI_CAP <- gsub(",",".",masterset$GNI_CAP)
masterset$GNI_CAP <- gsub(" ","",masterset$GNI_CAP)%>% as.numeric()

masterset$POPULATN <- gsub(",",".",masterset$POPULATN)
masterset$POPULATN <- gsub(" ","",masterset$POPULATN) %>% as.numeric()

# Manually fixing names

names(masterset)[which(names(masterset) == "TRDX352b")] <- "TRDEX352b" # These years are getting dropped.  
names(masterset)[which(names(masterset) == "TRDX200h")] <- "TRDEX200h"
names(masterset)[which(names(masterset) == "TRDX200m")] <- "TRDEX200m"
names(masterset)[which(names(masterset) == "TDX321sr")] <- "TRDEX321sr"
names(masterset)[which(names(masterset) == "TDX321sm")] <- "TRDEX321sm"
names(masterset)[which(names(masterset) == "TDX321yr")] <- "TRDEX321yr"

names(masterset)[which(names(masterset) == "TRDI200h")] <- "TRDIM200h"
names(masterset)[which(names(masterset) == "TRDI200m")] <- "TRDIM200m"
names(masterset)[which(names(masterset) == "TDI321sr")] <- "TRDIM321sr"
names(masterset)[which(names(masterset) == "TDI321sm")] <- "TRDIM321sm"
names(masterset)[which(names(masterset) == "TDI321yr")] <- "TRDIM321yr"
names(masterset)[which(names(masterset) == "TDI316SU")] <- "TRDIM316su"

masterset <- masterset %>% mutate(ODAG404 = as.numeric(ODAG404))

masterset <- masterset %>%
  mutate(across(ODAG201:ODAG501, ~ replace_na(.x, 0))) %>% # Replace NA with 0
  mutate(across(ODAG201:ODAG501, ~ pmax(.x, 0))) %>% # No negative numbers
  mutate(across(ODAG201:ODAG501, ~ as.numeric(.x))) %>% # Make these variables numeric
  rowwise() %>% 
  mutate(ODAGTOT200_501 = rowSums(across(ODAG201:ODAG501))) %>% 
  mutate(HHI = rowSums((across(ODAG201:ODAG501) / rowSums(across(ODAG201:ODAG501)))^2)) %>% 
  mutate(HHI = ifelse(ODAGTOT200_501 == 0, NA, HHI))

## Prepare data for analysis
masterset <- masterset %>% mutate(across(TRDEX351:TRDEX203, ~ as.numeric(.x))) %>% 
  mutate(across(TRDIM351:TRDIM203, ~ as.numeric(.x))) %>% 
  mutate(TRDEXtot = rowSums(pick(TRDEX351:TRDEX250, 
                                 TRDEX300:TRDEX285, 
                                 TRDEX280:TRDEX415,
                                 TRDEX100:TRDEX147,
                                 TRDEX577:TRDEX551,
                                 TRDEX563:TRDEX203),na.rm = TRUE),
         TRDIMtot = rowSums(pick(TRDIM351:TRDIM250,
                                 TRDIM300:TRDIM285,
                                 TRDIM280:TRDIM415,
                                 TRDIM100:TRDIM147,
                                 TRDIM577:TRDIM551,
                                 TRDIM563:TRDIM203),na.rm = TRUE)) %>% 
  mutate(ODAGtot = rowSums(pick(ODAG201:ODAG501), na.rm = T)) %>% 
  filter(ODAGtot >= 0) %>% 
  mutate(POPULATN = ifelse(POPULATN == -99, NA, POPULATN),
         logGNI = log(GNI, 10),
         logPOP = log(POPULATN,10),
         logTRDIMtot = log(TRDIMtot + 1,10),
         logTRDEXtot = log(TRDEXtot + 1,10), 
         logODAGtot = log(ODAGtot + 1, 10)) 

# Now create the lag variables
masterset <- masterset %>% arrange(CCODE, YEAR) %>% group_by(CCODE) %>% 
  mutate(TOTLIB1_lag1 = lag(TOTLIB1,1),
         TOTLIB1_lag2 = lag(TOTLIB1,2),
         TOTLIB1_lag3 = lag(TOTLIB1,3),
         POLITY_lag1 = lag(POLITY,1),
         POLITY_lag2 = lag(POLITY,2),
         POLITY_lag3 = lag(POLITY,3),
         POLITY2_lag1 = lag(POLITY2,1),
         POLITY2_lag2 = lag(POLITY2,2),
         POLITY2_lag3 = lag(POLITY2,3),
         V2x_Libdem_lag1 = lag(V2x_Libdem,1),
         V2x_Libdem_lag2 = lag(V2x_Libdem,2),
         V2x_Libdem_lag3 = lag(V2x_Libdem,3)
  ) %>% 
  ungroup()

```

```{r}
masterset %>% filter(YEAR == 2024) %>% arrange(ODAGtot) %>% select(COUNTRY, YEAR, ODAGtot) %>% head()

masterset %>% filter(YEAR >= 1990) %>% group_by(COUNTRY) %>% summarize(mn = mean(ODAGtot, na.rm = T)) %>% select(COUNTRY,mn) %>% head()
```

The distributions of the full model predictor variables and their log transformations are plotted below. The log-transformed variables all display a noticeably reduced right-skew, improving their performance and interpretation in the full models.

```{r}
masterset %>% 
  ggplot(aes(x = POPULATN)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Population Density\n of External Countries",
    x = "External Country Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = logPOP)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Population\n Density of External Countries",
    x = "Log-Transformed External Country Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = GNI)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Gross National Income (GNI)\n Density of External Countries",
    x = "External Country GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = logGNI)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Gross National Income (GNI)\n Density of External Countries",
    x = "Log-Transformed External Country GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = ODAGtot)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Official Development Assistance Gross (ODAG)\n Density of External Countries",
    x = "External Country ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = logODAGtot)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Official Development Assistance Gross\n (ODAG) Density of External Countries",
    x = "Log-Transformed External Country ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r echo = FALSE}
load("./ODAGmodels/mod0_POLITY2.RData")
load("./ODAGmodels/mod0_POLITY2_lag1.RData")
load("./ODAGmodels/mod0_POLITY2_lag2.RData")
load("./ODAGmodels/mod0_POLITY2_lag3.RData")
load("./ODAGmodels/mod1_POLITY2.RData")
load("./ODAGmodels/mod1_POLITY2_lag1.RData")
load("./ODAGmodels/mod1_POLITY2_lag2.RData")
load("./ODAGmodels/mod1_POLITY2_lag3.RData")

load("./ODAGmodels/mod0_TOTLIB1.RData")
load("./ODAGmodels/mod0_TOTLIB1_lag1.RData")
load("./ODAGmodels/mod0_TOTLIB1_lag2.RData")
load("./ODAGmodels/mod0_TOTLIB1_lag3.RData")
load("./ODAGmodels/mod1_TOTLIB1.RData")
load("./ODAGmodels/mod1_TOTLIB1_lag1.RData")
load("./ODAGmodels/mod1_TOTLIB1_lag2.RData")
load("./ODAGmodels/mod1_TOTLIB1_lag3.RData")

load("./ODAGmodels/mod0_V2x_Libdem.RData")
load("./ODAGmodels/mod0_V2x_Libdem_lag1.RData")
load("./ODAGmodels/mod0_V2x_Libdem_lag2.RData")
load("./ODAGmodels/mod0_V2x_Libdem_lag3.RData")
load("./ODAGmodels/mod1_V2x_Libdem.RData")
load("./ODAGmodels/mod1_V2x_Libdem_lag1.RData")
load("./ODAGmodels/mod1_V2x_Libdem_lag2.RData")
load("./ODAGmodels/mod1_V2x_Libdem_lag3.RData")
```

Below are the summaries for the reduced models for ODAG from external countries. The $\hat{\beta}$ coefficients are starred by significance as denoted in each table. Below each coefficient is their respective standard error.

```{r}

## REDUCED MODEL SUMMARIES

library(modelsummary)
library(tinytable)

mod0_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod0_V2x_Libdem,
    "One-Year Lag" = mod0_V2x_Libdem_lag1,
    "Two-Year Lag" = mod0_V2x_Libdem_lag2,
    "Three-Year Lag" = mod0_V2x_Libdem_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "V2x_Libdem", "V2x_Libdem_lag1", "V2x_Libdem_lag2", "V2x_Libdem_lag3", "SD (Intercept YEAR)", "SD (Intercept CCODE)", 
    "SD (Observations)"
  ),
  title = "Reduced Model Summary for V2X_LIBDEM From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  ) %>%
  group_tt(i = list(
    "Performance" = 2,  # Inserts header before row index 2 (hp)
    "Controls"    = 4   # Inserts header before row index 4 (qsec)
  ))

mod0_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod0_POLITY2,
    "One-Year Lag" = mod0_POLITY2_lag1,
    "Two-Year Lag" = mod0_POLITY2_lag2,
    "Three-Year Lag" = mod0_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "POLITY2", "POLITY2_lag1", "POLITY2_lag2", "POLITY2_lag3", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Reduced Model Summary for POLITY2 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod0_TOTLIB1,
    "One-Year Lag" = mod0_TOTLIB1_lag1,
    "Two-Year Lag" = mod0_TOTLIB1_lag2,
    "Three-Year Lag" = mod0_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "TOTLIB1", "TOTLIB1_lag1", "TOTLIB1_lag2", "TOTLIB1_lag3", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for TOTLIB1 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

```

Below are the summaries for the full models for ODAG from external countries. As with the reduced model summaries, the $\hat{\beta}$ coefficients are starred by significance as denoted in each table, with their respective standard error below.

```{r}

## FULL MODEL SUMMARIES

mod1_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod1_V2x_Libdem,
    "One-Year Lag" = mod1_V2x_Libdem_lag1,
    "Two-Year Lag" = mod1_V2x_Libdem_lag2,
    "Three-Year Lag" = mod1_V2x_Libdem_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "V2x_Libdem", "V2x_Libdem_lag1", "V2x_Libdem_lag2", "V2x_Libdem_lag3", "logPOP", "I(logPOP^2)", "I(logPOP^3)",
    "logGNI", "I(logGNI^2)", "logODAGtot", "I(logODAGtot^2)", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for V2X_LIBDEM From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod1_POLITY2,
    "One-Year Lag" = mod1_POLITY2_lag1,
    "Two-Year Lag" = mod1_POLITY2_lag2,
    "Three-Year Lag" = mod1_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "POLITY2", "POLITY2_lag1", "POLITY2_lag2", "POLITY2_lag3", "logPOP", "I(logPOP^2)", "I(logPOP^3)",
    "logGNI", "I(logGNI^2)", "logODAGtot", "I(logODAGtot^2)", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for POLITY2 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod1_TOTLIB1,
    "One-Year Lag" = mod1_TOTLIB1_lag1,
    "Two-Year Lag" = mod1_TOTLIB1_lag2,
    "Three-Year Lag" = mod1_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "TOTLIB1", "TOTLIB1_lag1", "TOTLIB1_lag2", "TOTLIB1_lag3", "logPOP", "I(logPOP^2)", "I(logPOP^3)",
    "logGNI", "I(logGNI^2)", "logODAGtot", "I(logODAGtot^2)", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for TOTLIB1 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

```

```{r}
load("./ODAGPRIVATEmodels/mod0_private_POLITY2.RData")
load("./ODAGPRIVATEmodels/mod0_private_POLITY2_lag1.RData")
load("./ODAGPRIVATEmodels/mod0_private_POLITY2_lag2.RData")
load("./ODAGPRIVATEmodels/mod0_private_POLITY2_lag3.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2_lag1.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2_lag2.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2_lag3.RData")

load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1.RData")
load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1_lag1.RData")
load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1_lag2.RData")
load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1_lag3.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1_lag1.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1_lag2.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1_lag3.RData")

load("./ODAGPRIVATEmodels/mod0_V2x_Libdem.RData")
load("./ODAGPRIVATEmodels/mod0_V2x_Libdem_lag1.RData")
load("./ODAGPRIVATEmodels/mod0_private_V2x_Libdem_lag2.RData")
load("./ODAGPRIVATEmodels/mod0_private_V2x_Libdem_lag3.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem_lag1.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem_lag2.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem_lag3.RData")
```

Below are the summaries for the reduced models for ODAG from private organizations The $\hat{\beta}$ coefficients are starred by significance as denoted in each table. Below each coefficient is their respective standard error.

```{r}

## REDUCED MODEL SUMMARIES

library(modelsummary)
library(tinytable)

mod0_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod0_private_V2x_Libdem,
    "One-Year Lag" = mod0_private_V2x_Libdem_lag1,
    "Two-Year Lag" = mod0_private_V2x_Libdem_lag2,
    "Three-Year Lag" = mod0_private_V2x_Libdem_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "V2x_Libdem", "V2x_Libdem_lag1", "V2x_Libdem_lag2", "V2x_Libdem_lag3", "SD (Intercept YEAR)", "SD (Intercept CCODE)", 
    "SD (Observations)"
  ),
  title = "Reduced Model Summary for V2X_LIBDEM From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  ) %>%
  group_tt(i = list(
    "Performance" = 2,  # Inserts header before row index 2 (hp)
    "Controls"    = 4   # Inserts header before row index 4 (qsec)
  ))

mod0_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod0_private_POLITY2,
    "One-Year Lag" = mod0_private_POLITY2_lag1,
    "Two-Year Lag" = mod0_private_POLITY2_lag2,
    "Three-Year Lag" = mod0_private_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "POLITY2", "POLITY2_lag1", "POLITY2_lag2", "POLITY2_lag3", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Reduced Model Summary for POLITY2 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod0_private_TOTLIB1,
    "One-Year Lag" = mod0_private_TOTLIB1_lag1,
    "Two-Year Lag" = mod0_private_TOTLIB1_lag2,
    "Three-Year Lag" = mod0_private_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "TOTLIB1", "TOTLIB1_lag1", "TOTLIB1_lag2", "TOTLIB1_lag3", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for TOTLIB1 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

```

Below are the summaries for the full models for ODAG from private organizations As with the reduced model summaries, the $\hat{\beta}$ coefficients are starred by significance as denoted in each table, with their respective standard error below.

```{r}

## FULL MODEL SUMMARIES

mod1_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod1_private_V2x_Libdem,
    "One-Year Lag" = mod1_private_V2x_Libdem_lag1,
    "Two-Year Lag" = mod1_private_V2x_Libdem_lag2,
    "Three-Year Lag" = mod1_private_V2x_Libdem_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "V2x_Libdem", "V2x_Libdem_lag1", "V2x_Libdem_lag2", "V2x_Libdem_lag3", "logPOP", "I(logPOP^2)", "I(logPOP^3)",
    "logGNI", "I(logGNI^2)", "logODAGtot", "I(logODAGtot^2)", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for V2X_LIBDEM From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod1_private_POLITY2,
    "One-Year Lag" = mod1_private_POLITY2_lag1,
    "Two-Year Lag" = mod1_private_POLITY2_lag2,
    "Three-Year Lag" = mod1_private_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "POLITY2", "POLITY2_lag1", "POLITY2_lag2", "POLITY2_lag3", "logPOP", "I(logPOP^2)", "I(logPOP^3)",
    "logGNI", "I(logGNI^2)", "logODAGtot", "I(logODAGtot^2)", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for POLITY2 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod1_private_TOTLIB1,
    "One-Year Lag" = mod1_private_TOTLIB1_lag1,
    "Two-Year Lag" = mod1_private_TOTLIB1_lag2,
    "Three-Year Lag" = mod1_private_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  coef_map = c(
    "(Intercept)", "TOTLIB1", "TOTLIB1_lag1", "TOTLIB1_lag2", "TOTLIB1_lag3", "logPOP", "I(logPOP^2)", "I(logPOP^3)",
    "logGNI", "I(logGNI^2)", "logODAGtot", "I(logODAGtot^2)", "SD (Intercept YEAR)", "SD (Intercept CCODE)", "SD (Observations)"
  ),
  title = "Full Model Summary for TOTLIB1 From External Countries"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

```
