---
title: "ODAG Report"
author: "Gregory J. Matthews and Steven Pappas"
format: pdf
execute:
  echo: false
  message: false
  warning: false
editor: visual
date: "September 28, 2026"
---
<!-- Note:  let's not call it private.  Multilateral.  -->

# Overview

This analysis seeks to evaluate the relationship between an African country's official development assistance gross (ODAG) and their democracy score. ODAG measures the aid received by an African country from external countries and private organizations. (Note: In this report, we refer to ODAG received from other countries as ODAG and ODAG received from entities that are not countries are ODAGprivate.) We used democracy scores from Freedom House (TOTLIB1), the POLITY IV database (POLITY2), and the Liberal Democracy Index from the V-Dem Institute (V2x_Libdem). (Note: Here we only analyze POLITY2, whereas in previous reports we have analyzed both POLITY and POLITY2.)

This main analyses were split into a reduced and full model. The reduced model only considers democracy as a fixed effect, while including random intercepts for the African country and year. These random effects account for structural correlation between observations within the data structure.

The full model includes all of the parts of the reduced model while adding the African country's population, gross national income (GNI), total imports, total exports, colonial Past, region, and a cold war indicator variable. We applied a log transformation to GNI, population, imports, and exports due to their right skew.

## ODAG (Countries)

In the reduced models (Tables 1-3), all V2x_Libdem, POLITY2, and TOTLIB1 coefficients are significant at $\alpha$ = 0.05. In all cases, higher democracy scores were associated with larger levels of total ODAG.

In the full models (Table 4-6), all V2x_Libdem, POLITY2, and TOTLIB1 coefficients are significant at $\alpha$ = 0.05. In all cases, higher democracy scores were associated with high total ODAG. In addition, we see that total population, GNI, total imports, and the cold war indicator are all significant. Population and total imports were positively correlated with total ODAG whereas larger GNI was related to lower levels of ODAG. Finally, the cold war (pre-1992) is associated with lower total levels of ODAG.

## ODAG (Private)

In the reduced models (Tables 7-9), once again all V2x_Libdem, POLITY2, and TOTLIB1 coefficients are significant at $\alpha$ = 0.05. In all cases, higher democracy scores were associated with larger levels of total ODAG.

In the full models (Table 10-12), all V2x_Libdem, POLITY2, and TOTLIB1 coefficients are again significant at $\alpha$ = 0.05. In all cases, higher democracy scores were associated with high total ODAG. As before, we see that total population, GNI, total imports, and the cold war indicator are all significant. However, unlike the previous full models, total exports in also significant here. Population and total imports were positively correlated with total ODAG whereas larger GNI and total exports was related to lower levels of ODAG. Finally, the cold war indicator (pre-1992) is associated with lower total levels of ODAG.

# Models

## Reduced Model

The reduced model is described below, where the response $Y_{it}$ is ODAG for African country $i$ in year $t$. We applied a log transformation to ODAG for better model fit. The predictor $X_{1it}$ represents the democracy score of African country $i$ in year $t$.

In lagged models, the year $t$ changes units depending on the lag. For instance, a one-year lag would produce the model equation $\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$, where $X_{1i(t-1)}$ is the external country's democracy score in the prior year (year $t$-1).

$$Y_{it} \sim \text{N}(\mu_{it}, \sigma^2)$$

$$\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$$

$$\gamma_{0i} \sim \text{N}(0, \sigma_{\text{country}}^2)$$

$$\gamma_{0t} \sim \text{N}(0, \sigma_{\text{year}}^2)$$

# Full Model

Our full model equations are given below. They follow the same setup as the reduced model with the addition of the aforementioned transformed country characteristics. In lagged models, we only lagged the country's democracy score. For instance, a one-year lag would produce the model equation $\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1i(t-1)} + \ldots  + \gamma_{0i} + \gamma_{0t} + \epsilon_{it}$, where $X_{1i(t-1)}$ is the country's democracy score in the prior year (year $t$-1).

Additional predictors in this model include the African country's log-transformed GNI, population, and total ODAG. Quadratic terms were included for the log-transformed GNI, population, and total ODAG. The log-transformed population variable added a cubic term to capture further nonlinear tendencies.

$$Y_{it} \sim \text{N}(\mu_{it}, \sigma^2)$$

$$\log(\text{ODAG}_{it}) = \beta_0 + \beta_1X_{1ik} + \ldots + \gamma_{0i} + \gamma_{tk} + \epsilon_{it}$$

$$\gamma_{0i} \sim \text{N}(0, \sigma_{\text{country}}^2)$$

$$\gamma_{0t} \sim \text{N}(0, \sigma_{\text{year}}^2)$$

# Data Visualizations and Results

```{r}

library(tidyverse)
library(readxl)

## Cleaning data ##

masterset = read_csv("./data2026/MASTER DATASET - 9.10.2026.csv")

masterset = masterset %>%
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         across(where(is.numeric), ~ na_if(., -88)),
         across(where(is.numeric), ~ na_if(., -77)),
         across(where(is.numeric), ~ na_if(., -66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY),
         COLD_WAR = ifelse(YEAR >= 1992, 0, 1), 
         COLPAST1 = as.factor(COLPAST1),
         REGION = as.factor(REGION))

# Convert commas to periods. 
# It looks like commas are being used as the decimal.  
# Fix the nonsense formatting from excel. 

masterset$GNI <- gsub(",",".",masterset$GNI)
masterset$GNI <- gsub(" ","",masterset$GNI)%>% as.numeric()

masterset$GNI_CAP <- gsub(",",".",masterset$GNI_CAP)
masterset$GNI_CAP <- gsub(" ","",masterset$GNI_CAP)%>% as.numeric()

masterset$POPULATN <- gsub(",",".",masterset$POPULATN)
masterset$POPULATN <- gsub(" ","",masterset$POPULATN) %>% as.numeric()

# Manually fixing names

names(masterset)[which(names(masterset) == "TRDX352b")] <- "TRDEX352b" # These years are getting dropped.  
names(masterset)[which(names(masterset) == "TRDX200h")] <- "TRDEX200h"
names(masterset)[which(names(masterset) == "TRDX200m")] <- "TRDEX200m"
names(masterset)[which(names(masterset) == "TDX321sr")] <- "TRDEX321sr"
names(masterset)[which(names(masterset) == "TDX321sm")] <- "TRDEX321sm"
names(masterset)[which(names(masterset) == "TDX321yr")] <- "TRDEX321yr"

names(masterset)[which(names(masterset) == "TRDI200h")] <- "TRDIM200h"
names(masterset)[which(names(masterset) == "TRDI200m")] <- "TRDIM200m"
names(masterset)[which(names(masterset) == "TDI321sr")] <- "TRDIM321sr"
names(masterset)[which(names(masterset) == "TDI321sm")] <- "TRDIM321sm"
names(masterset)[which(names(masterset) == "TDI321yr")] <- "TRDIM321yr"
names(masterset)[which(names(masterset) == "TDI316SU")] <- "TRDIM316su"

masterset <- masterset %>% mutate(ODAG404 = as.numeric(ODAG404))

#ODAG Country and HHI
masterset <- masterset %>%
  mutate(across(ODAG201:ODAG501, ~ replace_na(.x, 0))) %>% # Replace NA with 0
  mutate(across(ODAG201:ODAG501, ~ pmax(.x, 0))) %>% # No negative numbers
  mutate(across(ODAG201:ODAG501, ~ as.numeric(.x))) %>% # Make these variables numeric
  rowwise() %>% 
  mutate(ODAGTOT200_501 = rowSums(across(ODAG201:ODAG501))) %>% 
  mutate(HHI = rowSums((across(ODAG201:ODAG501) / rowSums(across(ODAG201:ODAG501)))^2)) %>% 
  mutate(HHI = ifelse(ODAGTOT200_501 == 0, NA, HHI))

#Masterset private
masterset <- masterset %>% 
  mutate(across(c(ODAG600, ODAG601, ODAG609, ODAG610, ODAG613:ODAGARBC, ODAGARBA:ODAGIAEA, odagrdbtot, 
                                           odagfao:odagwbtot, odagaf:odaggggi), ~ as.numeric(.x))) %>% # Make these variables numeric
  mutate(across(c(ODAG600, ODAG601, ODAG609, ODAG610, ODAG613:ODAGARBC, ODAGARBA:ODAGIAEA, odagrdbtot, 
                  odagfao:odagwbtot, odagaf:odaggggi), ~ replace_na(.x, 0))) %>% # Replace NA with 0
  mutate(across(c(ODAG600, ODAG601, ODAG609, ODAG610, ODAG613:ODAGARBC, ODAGARBA:ODAGIAEA, odagrdbtot, 
                  odagfao:odagwbtot, odagaf:odaggggi), ~ pmax(.x, 0))) %>% # No negative numbers
  rowwise() %>% 
  mutate(ODAGTOT200_501 = rowSums(across(ODAG201:ODAG501))) %>% 
  mutate(HHI = rowSums((across(ODAG201:ODAG501) / rowSums(across(ODAG201:ODAG501)))^2)) %>% 
  mutate(HHI = ifelse(ODAGTOT200_501 == 0, NA, HHI))

## Prepare data for analysis
masterset <- masterset %>% mutate(across(TRDEX351:TRDEX203, ~ as.numeric(.x))) %>% 
  mutate(across(TRDIM351:TRDIM203, ~ as.numeric(.x))) %>% 
  mutate(TRDEXtot = rowSums(pick(TRDEX351:TRDEX250, 
                                 TRDEX300:TRDEX285, 
                                 TRDEX280:TRDEX415,
                                 TRDEX100:TRDEX147,
                                 TRDEX577:TRDEX551,
                                 TRDEX563:TRDEX203),na.rm = TRUE),
         TRDIMtot = rowSums(pick(TRDIM351:TRDIM250,
                                 TRDIM300:TRDIM285,
                                 TRDIM280:TRDIM415,
                                 TRDIM100:TRDIM147,
                                 TRDIM577:TRDIM551,
                                 TRDIM563:TRDIM203),na.rm = TRUE)) %>% 
  mutate(ODAGtot = rowSums(pick(ODAG201:ODAG501), na.rm = T)) %>% mutate(ODAGtot_private = rowSums(pick(
    c(
      ODAG600,
      ODAG601,
      ODAG609,
      ODAG610,
      ODAG613:ODAGARBC,
      ODAGARBA:ODAGIAEA,
      odagrdbtot,
      odagfao:odagwbtot,
      odagaf:odaggggi
    )
  ), na.rm = T)) %>% 
  filter(ODAGtot >= 0 & ODAGtot_private >= 0) %>% 
  mutate(POPULATN = ifelse(POPULATN == -99, NA, POPULATN),
         logGNI = log(GNI, 10),
         logPOP = log(POPULATN,10),
         logTRDIMtot = log(TRDIMtot + 1,10),
         logTRDEXtot = log(TRDEXtot + 1,10), 
         logODAGtot = log(ODAGtot + 1, 10)) 

# Now create the lag variables
masterset <- masterset %>% arrange(CCODE, YEAR) %>% group_by(CCODE) %>% 
  mutate(TOTLIB1_lag1 = lag(TOTLIB1,1),
         TOTLIB1_lag2 = lag(TOTLIB1,2),
         TOTLIB1_lag3 = lag(TOTLIB1,3),
         POLITY_lag1 = lag(POLITY,1),
         POLITY_lag2 = lag(POLITY,2),
         POLITY_lag3 = lag(POLITY,3),
         POLITY2_lag1 = lag(POLITY2,1),
         POLITY2_lag2 = lag(POLITY2,2),
         POLITY2_lag3 = lag(POLITY2,3),
         V2x_Libdem_lag1 = lag(V2x_Libdem,1),
         V2x_Libdem_lag2 = lag(V2x_Libdem,2),
         V2x_Libdem_lag3 = lag(V2x_Libdem,3)
  ) %>% 
  ungroup()

```

The distributions of the full model predictor variables and their log transformations are plotted below. The log-transformed variables all display a noticeably reduced right-skew, improving their performance and interpretation in the full models.

```{r}
masterset %>% 
  ggplot(aes(x = POPULATN)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Population",
    x = "Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = logPOP)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Population",
    x = "Log-Transformed Population"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = GNI)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Gross National Income (GNI)\n Density",
    x = "GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = logGNI)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Gross National Income (GNI) Density",
    x = "Log-Transformed GNI"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = ODAGtot)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Official Development Assistance\n Gross (ODAG) Density ",
    x = "ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>% 
  ggplot(aes(x = logODAGtot)) + 
  geom_density(fill = "#7bffff") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Log-Transformed Official Developmen\n Assistance Gross (ODAG) Density",
    x = "Log-Transformed ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  )
```

```{r}
masterset %>%  
  ggplot(aes(x = logODAGtot, color = as.factor(COLD_WAR))) + geom_density() +
  labs(
    title = "Log ODAG distribution pre- and post-cold war",
    x = "Log-Transformed ODAG"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  ) 
```

```{r}

masterset %>% mutate(logODAGtot_private = log(ODAGtot_private +1,10)) %>% 
  ggplot(aes(x = logODAGtot_private, color = as.factor(COLD_WAR))) + geom_density() +
  labs(
    title = "Log ODAG Private distribution pre- and post-cold war",
    x = "Log-Transformed ODAG Private"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")
  ) 
```

```{r echo = FALSE}
load("./ODAGmodels/mod0_POLITY2.RData")
load("./ODAGmodels/mod0_POLITY2_lag1.RData")
load("./ODAGmodels/mod0_POLITY2_lag2.RData")
load("./ODAGmodels/mod0_POLITY2_lag3.RData")
load("./ODAGmodels/mod1_POLITY2.RData")
load("./ODAGmodels/mod1_POLITY2_lag1.RData")
load("./ODAGmodels/mod1_POLITY2_lag2.RData")
load("./ODAGmodels/mod1_POLITY2_lag3.RData")

load("./ODAGmodels/mod0_TOTLIB1.RData")
load("./ODAGmodels/mod0_TOTLIB1_lag1.RData")
load("./ODAGmodels/mod0_TOTLIB1_lag2.RData")
load("./ODAGmodels/mod0_TOTLIB1_lag3.RData")
load("./ODAGmodels/mod1_TOTLIB1.RData")
load("./ODAGmodels/mod1_TOTLIB1_lag1.RData")
load("./ODAGmodels/mod1_TOTLIB1_lag2.RData")
load("./ODAGmodels/mod1_TOTLIB1_lag3.RData")

load("./ODAGmodels/mod0_V2x_Libdem.RData")
load("./ODAGmodels/mod0_V2x_Libdem_lag1.RData")
load("./ODAGmodels/mod0_V2x_Libdem_lag2.RData")
load("./ODAGmodels/mod0_V2x_Libdem_lag3.RData")
load("./ODAGmodels/mod1_V2x_Libdem.RData")
load("./ODAGmodels/mod1_V2x_Libdem_lag1.RData")
load("./ODAGmodels/mod1_V2x_Libdem_lag2.RData")
load("./ODAGmodels/mod1_V2x_Libdem_lag3.RData")
```

Summaries for the reduced and full models for ODAG are shown with the regression coefficient estimates in the column labeled "Est." starred by significance as denoted in the legend below. each table. Next to each coefficient estimate is their respective standard error.

# ODAG Results

```{r}

## REDUCED MODEL SUMMARIES

library(modelsummary)
library(tinytable)

mod0_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod0_V2x_Libdem,
    "One-Year Lag" = mod0_V2x_Libdem_lag1,
    "Two-Year Lag" = mod0_V2x_Libdem_lag2,
    "Three-Year Lag" = mod0_V2x_Libdem_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)",
    "V2x_Libdem",
    "V2x_Libdem_lag1",
    "V2x_Libdem_lag2",
    "V2x_Libdem_lag3",
    "SD (Intercept YEAR)",
    "SD (Intercept CCODE)",
    "SD (Observations)"
  ),
  title = "ODAG: Reduced Model Summary for V2X_LIBDEM"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod0_POLITY2,
    "One-Year Lag" = mod0_POLITY2_lag1,
    "Two-Year Lag" = mod0_POLITY2_lag2,
    "Three-Year Lag" = mod0_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)",
    "POLITY2",
    "POLITY2_lag1",
    "POLITY2_lag2",
    "POLITY2_lag3",
    "SD (Intercept YEAR)",
    "SD (Intercept CCODE)",
    "SD (Observations)"
  ),
  title = "ODAG: Reduced Model Summary for POLITY2"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod0_TOTLIB1,
    "One-Year Lag" = mod0_TOTLIB1_lag1,
    "Two-Year Lag" = mod0_TOTLIB1_lag2,
    "Three-Year Lag" = mod0_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)",
    "TOTLIB1",
    "TOTLIB1_lag1",
    "TOTLIB1_lag2",
    "TOTLIB1_lag3",
    "SD (Intercept YEAR)",
    "SD (Intercept CCODE)",
    "SD (Observations)"
  ),
  title = "ODAG: Reduced Model Summary for TOTLIB1"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_summary_V2X_LIBDEM
mod0_summary_POLITY2
mod0_summary_TOTLIB1

```

Below are the summaries for the full models for ODAG from external countries. As with the reduced model summaries, the $\hat{\beta}$ coefficients are starred by significance as denoted in each table, with their respective standard error below.

```{r}

## FULL MODEL SUMMARIES

mod1_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod1_V2x_Libdem,
    "One-Year Lag" = mod1_V2x_Libdem_lag1,
    "Two-Year Lag" = mod1_V2x_Libdem_lag2,
    "Three-Year Lag" = mod1_V2x_Libdem_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
     "(Intercept)" = "Intercept",
    "V2x_Libdem" = "V2x_Libdem",
    "V2x_Libdem_lag1" = "V2x_Libdem_lag1",
    "V2x_Libdem_lag2" = "V2x_Libdem_lag2",
    "V2x_Libdem_lag3" = "V2x_Libdem_lag3",
    "logPOP" = "logPOP",
    "logGNI" = "logGNI",
    "logTRDIMtot" = "logTRDIMtot",
    "logTRDEXtot" = "logTRDEXtot",
    "COLPAST12" = "COL_British",
    "COLPAST13" = "COL_Portuguese",
    "COLPAST14" = "COL_Spanish",
    "COLPAST15" = "COL_Italian",
    "COLPAST16" = "COL_Belgian",
    "COLPAST17" = "COL_German",
    "COLPAST18" = "COL_US",
    "COLPAST19" = "COL_None",
    "COLPAST110" = "COL_Unique",
    "REGION2" = "REG_E_Africa",
    "REGION3" = "REG_S_Africa",
    "REGION4" = "REG_C_Africa",
    "REGION5" = "REG_W_Africa",
    "COLD_WAR" = "COLD_WAR",
    "SD (Intercept YEAR)" = "SD (Intercept YEAR)",
    "SD (Intercept CCODE)" = "SD (Intercept CCODE)",
    "SD (Observations)" = "SD (Observations)"
  ),
  title = "ODAG: Full Model Summary for V2X_LIBDEM"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod1_POLITY2,
    "One-Year Lag" = mod1_POLITY2_lag1,
    "Two-Year Lag" = mod1_POLITY2_lag2,
    "Three-Year Lag" = mod1_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)" = "Intercept",
    "POLITY2" = "POLITY2",
    "POLITY2_lag1" = "POLITY2_lag1",
    "POLITY2_lag2" = "POLITY2_lag2",
    "POLITY2_lag3" = "POLITY2_lag3",
    "logPOP" = "logPOP",
    "logGNI" = "logGNI",
    "logTRDIMtot" = "logTRDIMtot",
    "logTRDEXtot" = "logTRDEXtot",
    "COLPAST12" = "COL_British",
    "COLPAST13" = "COL_Portuguese",
    "COLPAST14" = "COL_Spanish",
    "COLPAST15" = "COL_Italian",
    "COLPAST16" = "COL_Belgian",
    "COLPAST17" = "COL_German",
    "COLPAST18" = "COL_US",
    "COLPAST19" = "COL_None",
    "COLPAST110" = "COL_Unique",
    "REGION2" = "REG_E_Africa",
    "REGION3" = "REG_S_Africa",
    "REGION4" = "REG_C_Africa",
    "REGION5" = "REG_W_Africa",
    "COLD_WAR" = "COLD_WAR",
    "SD (Intercept YEAR)" = "SD (Intercept YEAR)",
    "SD (Intercept CCODE)" = "SD (Intercept CCODE)",
    "SD (Observations)" = "SD (Observations)"
  ),
  title = "ODAG: Full Model Summary for POLITY2"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod1_TOTLIB1,
    "One-Year Lag" = mod1_TOTLIB1_lag1,
    "Two-Year Lag" = mod1_TOTLIB1_lag2,
    "Three-Year Lag" = mod1_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)" = "Intercept",
    "TOTLIB1" = "TOTLIB1",
    "TOTLIB1_lag1" = "TOTLIB1_lag1",
    "TOTLIB1_lag2" = "TOTLIB1_lag2",
    "TOTLIB1_lag3" = "TOTLIB1_lag3",
    "logPOP" = "logPOP",
    "logGNI" = "logGNI",
    "logTRDIMtot" = "logTRDIMtot",
    "logTRDEXtot" = "logTRDEXtot",
    "COLPAST12" = "COL_British",
    "COLPAST13" = "COL_Portuguese",
    "COLPAST14" = "COL_Spanish",
    "COLPAST15" = "COL_Italian",
    "COLPAST16" = "COL_Belgian",
    "COLPAST17" = "COL_German",
    "COLPAST18" = "COL_US",
    "COLPAST19" = "COL_None",
    "COLPAST110" = "COL_Unique",
    "REGION2" = "REG_E_Africa",
    "REGION3" = "REG_S_Africa",
    "REGION4" = "REG_C_Africa",
    "REGION5" = "REG_W_Africa",
    "COLD_WAR" = "COLD_WAR",
    "SD (Intercept YEAR)" = "SD (Intercept YEAR)",
    "SD (Intercept CCODE)" = "SD (Intercept CCODE)",
    "SD (Observations)" = "SD (Observations)"
  ),
  title = "ODAG: Full Model Summary for TOTLIB1"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_summary_V2X_LIBDEM
mod1_summary_POLITY2
mod1_summary_TOTLIB1
```

```{r}
load("./ODAGPRIVATEmodels/mod0_private_POLITY2.RData")
load("./ODAGPRIVATEmodels/mod0_private_POLITY2_lag1.RData")
load("./ODAGPRIVATEmodels/mod0_private_POLITY2_lag2.RData")
load("./ODAGPRIVATEmodels/mod0_private_POLITY2_lag3.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2_lag1.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2_lag2.RData")
load("./ODAGPRIVATEmodels/mod1_private_POLITY2_lag3.RData")

load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1.RData")
load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1_lag1.RData")
load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1_lag2.RData")
load("./ODAGPRIVATEmodels/mod0_private_TOTLIB1_lag3.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1_lag1.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1_lag2.RData")
load("./ODAGPRIVATEmodels/mod1_private_TOTLIB1_lag3.RData")

load("./ODAGPRIVATEmodels/mod0_private_V2x_Libdem.RData")
load("./ODAGPRIVATEmodels/mod0_private_V2x_Libdem_lag1.RData")
load("./ODAGPRIVATEmodels/mod0_private_V2x_Libdem_lag2.RData")
load("./ODAGPRIVATEmodels/mod0_private_V2x_Libdem_lag3.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem_lag1.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem_lag2.RData")
load("./ODAGPRIVATEmodels/mod1_private_V2x_Libdem_lag3.RData")
```

# ODAG Private Results

```{r}

## REDUCED MODEL SUMMARIES

library(modelsummary)
library(tinytable)

mod0_private_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod0_private_V2x_Libdem,
    "One-Year Lag" = mod0_private_V2x_Libdem_lag1,
    "Two-Year Lag" = mod0_private_V2x_Libdem_lag2,
    "Three-Year Lag" = mod0_private_V2x_Libdem_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)",
    "V2x_Libdem",
    "V2x_Libdem_lag1",
    "V2x_Libdem_lag2",
    "V2x_Libdem_lag3",
    "SD (Intercept YEAR)",
    "SD (Intercept CCODE)",
    "SD (Observations)"
  ),
  title = "ODAG Private: Reduced Model Summary for V2X_LIBDEM "
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_private_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod0_private_POLITY2,
    "One-Year Lag" = mod0_private_POLITY2_lag1,
    "Two-Year Lag" = mod0_private_POLITY2_lag2,
    "Three-Year Lag" = mod0_private_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)",
    "POLITY2",
    "POLITY2_lag1",
    "POLITY2_lag2",
    "POLITY2_lag3",
    "SD (Intercept YEAR)",
    "SD (Intercept CCODE)",
    "SD (Observations)"
  ),
  title = "ODAG Private: Reduced Model Summary for POLITY2"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_private_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod0_private_TOTLIB1,
    "One-Year Lag" = mod0_private_TOTLIB1_lag1,
    "Two-Year Lag" = mod0_private_TOTLIB1_lag2,
    "Three-Year Lag" = mod0_private_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)",
    "TOTLIB1",
    "TOTLIB1_lag1",
    "TOTLIB1_lag2",
    "TOTLIB1_lag3",
    "SD (Intercept YEAR)",
    "SD (Intercept CCODE)",
    "SD (Observations)"
  ),
  title = "ODAG Private: Full Model Summary for TOTLIB1"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod0_private_summary_V2X_LIBDEM
mod0_private_summary_POLITY2
mod0_private_summary_TOTLIB1
```

Below are the summaries for the full models for ODAG from private organizations As with the reduced model summaries, the $\hat{\beta}$ coefficients are starred by significance as denoted in each table, with their respective standard error below.

```{r}

## FULL MODEL SUMMARIES

mod1_private_summary_V2X_LIBDEM <- modelsummary(
  models = list(
    "Unlagged" = mod1_private_V2x_Libdem,
    "One-Year Lag" = mod1_private_V2x_Libdem_lag1,
    "Two-Year Lag" = mod1_private_V2x_Libdem_lag2,
    "Three-Year Lag" = mod1_private_V2x_Libdem_lag3
  ),
  statistic = NULL,
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)" = "Intercept",
    "V2x_Libdem" = "V2x_Libdem",
    "V2x_Libdem_lag1" = "V2x_Libdem_lag1",
    "V2x_Libdem_lag2" = "V2x_Libdem_lag2",
    "V2x_Libdem_lag3" = "V2x_Libdem_lag3",
    "logPOP" = "logPOP",
    "logGNI" = "logGNI",
    "logTRDIMtot" = "logTRDIMtot",
    "logTRDEXtot" = "logTRDEXtot",
    "COLPAST12" = "COL_British",
    "COLPAST13" = "COL_Portuguese",
    "COLPAST14" = "COL_Spanish",
    "COLPAST15" = "COL_Italian",
    "COLPAST16" = "COL_Belgian",
    "COLPAST17" = "COL_German",
    "COLPAST18" = "COL_US",
    "COLPAST19" = "COL_None",
    "COLPAST110" = "COL_Unique",
    "REGION2" = "REG_E_Africa",
    "REGION3" = "REG_S_Africa",
    "REGION4" = "REG_C_Africa",
    "REGION5" = "REG_W_Africa",
    "COLD_WAR" = "COLD_WAR",
    "SD (Intercept YEAR)" = "SD (Intercept YEAR)",
    "SD (Intercept CCODE)" = "SD (Intercept CCODE)",
    "SD (Observations)" = "SD (Observations)"
  ),
  title = "ODAG Private: Full Model Summary for V2X_LIBDEM"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  ) %>%  theme_tinytable(width = 0.5)

mod1_private_summary_POLITY2 <- modelsummary(
  models = list(
    "Unlagged" = mod1_private_POLITY2,
    "One-Year Lag" = mod1_private_POLITY2_lag1,
    "Two-Year Lag" = mod1_private_POLITY2_lag2,
    "Three-Year Lag" = mod1_private_POLITY2_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)" = "Intercept",
    "POLITY2" = "POLITY2",
    "POLITY2_lag1" = "POLITY2_lag1",
    "POLITY2_lag2" = "POLITY2_lag2",
    "POLITY2_lag3" = "POLITY2_lag3",
    "logPOP" = "logPOP",
    "logGNI" = "logGNI",
    "logTRDIMtot" = "logTRDIMtot",
    "logTRDEXtot" = "logTRDEXtot",
    "COLPAST12" = "COL_British",
    "COLPAST13" = "COL_Portuguese",
    "COLPAST14" = "COL_Spanish",
    "COLPAST15" = "COL_Italian",
    "COLPAST16" = "COL_Belgian",
    "COLPAST17" = "COL_German",
    "COLPAST18" = "COL_US",
    "COLPAST19" = "COL_None",
    "COLPAST110" = "COL_Unique",
    "REGION2" = "REG_E_Africa",
    "REGION3" = "REG_S_Africa",
    "REGION4" = "REG_C_Africa",
    "REGION5" = "REG_W_Africa",
    "COLD_WAR" = "COLD_WAR",
    "SD (Intercept YEAR)" = "SD (Intercept YEAR)",
    "SD (Intercept CCODE)" = "SD (Intercept CCODE)",
    "SD (Observations)" = "SD (Observations)"
  ),
  title = "ODAG Private: Full Model Summary for POLITY2"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_private_summary_TOTLIB1 <- modelsummary(
  models = list(
    "Unlagged" = mod1_private_TOTLIB1,
    "One-Year Lag" = mod1_private_TOTLIB1_lag1,
    "Two-Year Lag" = mod1_private_TOTLIB1_lag2,
    "Three-Year Lag" = mod1_private_TOTLIB1_lag3
  ),
  stars = T,
  gof_omit = ".",
  shape = term ~ model + statistic,
  coef_map = c(
    "(Intercept)" = "Intercept",
    "TOTLIB1" = "TOTLIB1",
    "TOTLIB1_lag1" = "TOTLIB1_lag1",
    "TOTLIB1_lag2" = "TOTLIB1_lag2",
    "TOTLIB1_lag3" = "TOTLIB1_lag3",
    "logPOP" = "logPOP",
    "logGNI" = "logGNI",
    "logTRDIMtot" = "logTRDIMtot",
    "logTRDEXtot" = "logTRDEXtot",
    "COLPAST12" = "COL_British",
    "COLPAST13" = "COL_Portuguese",
    "COLPAST14" = "COL_Spanish",
    "COLPAST15" = "COL_Italian",
    "COLPAST16" = "COL_Belgian",
    "COLPAST17" = "COL_German",
    "COLPAST18" = "COL_US",
    "COLPAST19" = "COL_None",
    "COLPAST110" = "COL_Unique",
    "REGION2" = "REG_E_Africa",
    "REGION3" = "REG_S_Africa",
    "REGION4" = "REG_C_Africa",
    "REGION5" = "REG_W_Africa",
    "COLD_WAR" = "COLD_WAR",
    "SD (Intercept YEAR)" = "SD (Intercept YEAR)",
    "SD (Intercept CCODE)" = "SD (Intercept CCODE)",
    "SD (Observations)" = "SD (Observations)"
  ),
  
  title = "ODAG Private: Full Model Summary for TOTLIB1"
) %>%
  style_tt(
    i = "caption",
    bold = TRUE,
    align = "c",
    fontsize = 1.5,
    bootstrap_class = "table caption-top"
  )

mod1_private_summary_V2X_LIBDEM
mod1_private_summary_POLITY2
mod1_private_summary_TOTLIB1

```
