---
title: "Embassies and Democracy - Resutls Only"
format: pdf
editor: visual
---

# BROAD QUESTION

Broad question: Does the process of democratization within African countries affect the formulation and implementation of African foreignpolicies.

## THERE ARE THREE DIFFERENT SETS OF STATISTICALLY BASED QUESTIONS (We address only question 1 here):

1.  African democracy and African embassies. Do greater levels of democratization of African countries lead to larger and more diversified embassy networks maintained by African countries overseas? Dependent variable: embassies maintained abroad (yes/no by country) in 1965, 1975, 1985, 1995, 2000, 2005, 2010, 2015, 2020, 2025 (use 2024 for 2025).
2.  African democracy and African trade. Do greater levels of democratization within African countries lead to larger and more diversified levels of trade imports and trade exports by African countries? Dependent variable: \$ amount of imports and exports annually for 1960 to 2022)
3.  African democracy and aid to Africa. Do greater levels of democratization within African countries lead to larger and more diversified levels of foreign aid to African countries? (Dependent variable:\$ amount of aid annually for every country in the world 1960 to 2021).

THUS, THREE DIFFERENT DEPENDENT VARIABLES:

1.  Total number and diversification of African embassies maintained abroad.
2.  Total amount and diversification of African trade imports and trade exports
3.  Total amount and diversification of foreign aid received by African countries

## THREE DIFFERENT VARIABLES OF AFRICAN DEMOCRACY AS INDEPENDENT VARIABLE

Three different variables of democracy (each with different inclusive dates) to use separately in the analyses as the independent variable:

1.  V-Dem democracy variable (1951-2024) Variable name in the dataset: v2x_LIBDEM. It ranges from 0 (worst) to 1 (best).
2.  Polity IV democracy variable (1948-2018) Variable name in the dataset: DEMOC. It ranges from -10 (worst) to +10 (best).
3.  Freedom House democracy variable (1972 - 2024) Variable name in the dataset: TOTLIB. It ranges from 1 (best) to 14 (worst). It is a combination of the following two variables, which people sometimes run separately: Civil liberties - Variable name in the dataset: -CIVLIB. It ranges from 1 (best) to 7 (worst). -Political rights: Variable name in the dataset: POLLIB. It ranges from 1 (best) to 7 (worst).

For each of the three democracy variables, will do a series of 4 tests with lags. -Test 1. Change in democracy score (no lag) -Test 2. Change in democracy score (1 year lag) -Test 3. Change in democracy score (2 year lag) -Test 4. Change in democracy score (3 year lag)

## CONTROL VARIABLES RELATED FOR AFRICAN COUNTRIES (AFRICAN FACTORS)

-African GNI OR GNI per capita (logged?) -African Population (size in millions) - Region of Africa (1= North Africa, 2 = East Africa, 3 = Southern Africa, 4= Central Africa, 5 = West Africa) - African Colonial Past (Colpast2) (1 = French, 2 = British, 3 = Portuguese, 4 = Spanish, 5 = Italian, 6 = Belgian, 7 = German, 8 = United States, 9 = Not colony, 10 = unique) - African Ideology (1 = capitalist, 2 = socialist, 3 = Marxist) - African Historical Period - Entire independence era - Cold War era (1945-1989) - Post-Cold War era (1990-present)

## PULL FACTORS—CHARACTERISTICS OF OTHER NON-AFRICAN COUNTRIES OF THE WORLD—JUST FOR THE EMBASSSY QUESTION

-   Level of democracy (Freedom House)
-   Level of democracy (Polity IV)
-   Level of democracy (V-dem) These are in the data set for the African countries, but need to be added for the rest of the world.
-   GNI
-   GNI per capita
-   Population
-   Imports
-   Exports
-   Foreign Aid

FOR THE THREE SETS OF STATISTICALLY BASED QUESTIONS, LET’S START WITH THE EMBASSIES (ABOVE QUESTION #1 FIRST)

```{r message = FALSE, warning=FALSE, echo = FALSE}
library(tidyverse)
library(readxl)
library(lme4)

masterset = read_csv("./data/Master 08-28-2025 AFP excel dataset-3.xlsx - AFRSdata.csv")

restofworld = read_excel("./old_data/Rest of the World.xlsx")

#Data cleaning
masterset = masterset %>%
  mutate(across(where(is.numeric), ~ na_if(., -99)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY))

#Convert commas to periods. 
#it looks like commas are being used as the decimal.  
#Fix the nonsense formatting from excel. 
masterset$GNI <- gsub(",",".",masterset$GNI)
masterset$GNI <- gsub(" ","",masterset$GNI)%>% as.numeric()

masterset$GNI_CAP <- gsub(",",".",masterset$GNI_CAP)
masterset$GNI_CAP <- gsub(" ","",masterset$GNI_CAP)%>% as.numeric()

masterset$POPULATN <- gsub(",",".",masterset$POPULATN)
masterset$POPULATN <- gsub(" ","",masterset$POPULATN) %>% as.numeric()


#Count the embassies
#names(masterset)
masterset <- masterset %>% mutate(N_EMBASSY = select(., C099:C572) %>% rowSums(na.rm = T))

#Preparing data for modeling
masterset <- masterset %>% mutate(YEAR1965 = YEAR - 1965)

#Filter out only years with embassy data
keep_years <- masterset %>% group_by(YEAR) %>% summarize(N_EMBASSY = sum(N_EMBASSY)) %>% filter(N_EMBASSY > 0) %>% pull(YEAR)

#Define lagged variables
modelset <- masterset %>% mutate(DEMOC = case_when(DEMOC < 0 ~ NA,.default = DEMOC),
                                 GNI = case_when(GNI < 0 ~ NA,.default = GNI),
                                 REGION = case_when(REGION == 1 ~ "North",
                                                    REGION == 2 ~ "East",
                                                    REGION == 3 ~ "South",
                                                    REGION == 4 ~ "Central",
                                                    REGION == 5 ~ "West"))


modelset <- modelset %>% arrange(COUNTRY, YEAR) %>% group_by(COUNTRY)  %>% 
                              mutate(v2x_LIBDEM_lag1 = lag(v2x_LIBDEM,1),
                                 v2x_LIBDEM_lag2 = lag(v2x_LIBDEM,2),
                                 v2x_LIBDEM_lag3 = lag(v2x_LIBDEM,3),
                                 DEMOC_lag1 = lag(DEMOC,1),
                                 DEMOC_lag2 = lag(DEMOC,2),
                                 DEMOC_lag3 = lag(DEMOC,3),
                                 TOTLIB1_lag1 = lag(TOTLIB1,1),
                                 TOTLIB1_lag2 = lag(TOTLIB1,2),
                                 TOTLIB1_lag3 = lag(TOTLIB1,3),
                                 POLITY_lag1 = lag(POLITY,1),
                                 POLITY_lag2 = lag(POLITY,2),
                                 POLITY_lag3 = lag(POLITY,3)
                                 ) %>%  ungroup() %>%   filter(YEAR %in% keep_years & !is.na(COUNTRY)) %>% 
  select(COUNTRY, YEAR, N_EMBASSY, v2x_LIBDEM, DEMOC, TOTLIB1, POLITY,
         CIVLIB, POLLIB,GNI_CAP,GNI, REGION, COLPAST2, IDEOLOGY, POPULATN, v2x_LIBDEM_lag1:POLITY_lag3) %>% 
  mutate(AFR_HIST_PERIOD = case_when(YEAR <= 1989 ~ "Cold War",
                                     YEAR >= 1990 ~ "Post-Cold War"), 
         logGNI = log(GNI,10),
         logPOPULATN = log(POPULATN,10),
         COL2 = ifelse(COLPAST2 != 9, "Colony", "Not Colony"),
         REGION = relevel(factor(REGION), ref = "North"),
         YEAR1965 = YEAR-1965)


#Define change in embassies
modelset <- modelset %>% group_by(COUNTRY) %>% arrange(YEAR) %>% 
  mutate(DELTA_N_EMBASSY = N_EMBASSY - lag(N_EMBASSY),
         DELTA_N_YEARS = YEAR - lag(YEAR),
         DELTA_N_EMBASSY_PER_YEAR = DELTA_N_EMBASSY/DELTA_N_YEARS,
         DELTA_DEMOC = DEMOC - lag(DEMOC),
         DELTA_DEMOC_PER_YEAR = DELTA_DEMOC/DELTA_N_YEARS,
         DELTA_v2x_LIBDEM = v2x_LIBDEM - lag(v2x_LIBDEM),
         DELTA_v2x_LIBDEM_PER_YEAR = DELTA_v2x_LIBDEM/DELTA_N_YEARS,
         DELTA_TOTLIB1 = TOTLIB1 - lag(TOTLIB1),
         DELTA_TOTLIB1_PER_YEAR = DELTA_TOTLIB1/DELTA_N_YEARS,
         DELTA_logGNI = logGNI - lag(logGNI),
         DELTA_logGNI_PER_YEAR = DELTA_logGNI/DELTA_N_YEARS, 
         DELTA_logPOPULATN = logPOPULATN  - lag(logPOPULATN),
         DELTA_logPOPULATN_PER_YEAR = DELTA_logPOPULATN /DELTA_N_YEARS)

modelset %>% group_by(YEAR, DEMOC) %>% summarize(n = n())
modelset %>% ggplot(aes(x = factor(DEMOC))) + geom_bar() + facet_wrap(~YEAR) + theme_bw()
modelset %>% ggplot(aes(x = factor(TOTLIB1))) + geom_bar() + facet_wrap(~YEAR) + theme_bw()
modelset %>% ggplot(aes(x = factor(YEAR), y = v2x_LIBDEM)) + geom_boxplot() +theme_bw()



#EDA
modelset %>% ggplot(aes(x = YEAR, y = N_EMBASSY, group = COUNTRY)) + geom_line() + geom_point() + theme_bw() 

modelset %>% ggplot(aes(x = v2x_LIBDEM, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = v2x_LIBDEM_lag1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = v2x_LIBDEM_lag2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = v2x_LIBDEM_lag3, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()

modelset %>% ggplot(aes(x = DEMOC, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = DEMOC_lag1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = DEMOC_lag2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = DEMOC_lag3, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()

modelset %>% ggplot(aes(x = TOTLIB1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = TOTLIB1_lag1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = TOTLIB1_lag2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = TOTLIB1_lag3, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()

#Correlations
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,DEMOC, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM)$p.val)
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,DEMOC_lag1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag1)$p.val)
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,DEMOC_lag2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag2)$p.val)
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,DEMOC_lag3, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag3)$p.val)

modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM)$p.val)
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM_lag1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag1)$p.val)
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM_lag2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag2)$p.val)
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM_lag3, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag3)$p.val)

modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1)$p.val)
modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1_lag1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1_lag1)$p.val)
modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1_lag2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1_lag2)$p.val)
modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1_lag3, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1_lag3)$p.val)

```

```{r echo = FALSE}
library(data.table)
library(gt)

mod_TOTLIB1 <- glmer(N_EMBASSY ~ TOTLIB1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag1 <- glmer(N_EMBASSY ~ TOTLIB1_lag1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag2 <- glmer(N_EMBASSY ~ TOTLIB1_lag2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag3 <- glmer(N_EMBASSY ~ TOTLIB1_lag3 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1, parm = "TOTLIB1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag1, parm = "TOTLIB1_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag2, parm = "TOTLIB1_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag3, parm = "TOTLIB1_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod_POLITY <- glmer(N_EMBASSY ~ POLITY + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag1 <- glmer(N_EMBASSY ~ POLITY_lag1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag2 <- glmer(N_EMBASSY ~ POLITY_lag2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag3 <- glmer(N_EMBASSY ~ POLITY_lag3 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

POLITY_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY, parm = "POLITY", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag1, parm = "POLITY_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag2, parm = "POLITY_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag3, parm = "POLITY_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod_v2x_LIBDEM <- glmer(N_EMBASSY ~ v2x_LIBDEM + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag1 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag2 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag3 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag3 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM, parm = "v2x_LIBDEM", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag1, parm = "v2x_LIBDEM_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag2, parm = "v2x_LIBDEM_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag3, parm = "v2x_LIBDEM_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3,
  v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY") ~ "POLITY",
                         str_detect(var, "LIBDEM") ~ "LIBDEM"))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    Estimate = md("$\\beta$"),
    Estimate_exp = md("$e^{\\beta}$"),
    pval = md("$p$"),
    confidence = md("$\\beta: 95\\% CI$"),
    confidence_exp = md("$e^{\\beta}: 95\\% CI$")
  ) %>%
  tab_header(
    title = md("Reduced Model Parameters for **Democracy Scores** and Their **Lags**")
  ) 
```

```{r echo = FALSE}
library(data.table)
library(gt)

mod_TOTLIB1 <- glmer(N_EMBASSY ~ TOTLIB1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

mod_TOTLIB1_lag1 <- glmer(N_EMBASSY ~ TOTLIB1_lag1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag2 <- glmer(N_EMBASSY ~ TOTLIB1_lag2 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag3 <- glmer(N_EMBASSY ~ TOTLIB1_lag3 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1, parm = "TOTLIB1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag1, parm = "TOTLIB1_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag2, parm = "TOTLIB1_lag2", level = 0.95, method = "boot", nsim = 50)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag3, parm = "TOTLIB1_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod_POLITY <- glmer(N_EMBASSY ~ POLITY + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag1 <- glmer(N_EMBASSY ~ POLITY_lag1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag2 <- glmer(N_EMBASSY ~ POLITY_lag2 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag3 <- glmer(N_EMBASSY ~ POLITY_lag3 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

POLITY_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY, parm = "POLITY", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag1, parm = "POLITY_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag2, parm = "POLITY_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag3, parm = "POLITY_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod_v2x_LIBDEM <- glmer(N_EMBASSY ~ v2x_LIBDEM + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag1 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag2 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag2 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag3 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag3 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM, parm = "v2x_LIBDEM", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag1, parm = "v2x_LIBDEM_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag2, parm = "v2x_LIBDEM_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag3, parm = "v2x_LIBDEM_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3,
  v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY") ~ "POLITY",
                         str_detect(var, "LIBDEM") ~ "LIBDEM"))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    Estimate = md("$\\beta$"),
    Estimate_exp = md("$e^{\\beta}$"),
    pval = md("$p$"),
    confidence = md("$\\beta: 95\\% CI$"),
    confidence_exp = md("$e^{\\beta}: 95\\% CI$")
  ) %>%
  tab_header(
    title = md("Full Model Parameters for **Democracy Scores** and Their **Lags**")
  )
```

```{r}

## DELTA MODELS ##

# Data #

modelset_delta <- modelset %>% group_by(COUNTRY) %>% arrange(YEAR) %>% 
  mutate(DELTA_N_EMBASSY = N_EMBASSY - lag(N_EMBASSY),
         DELTA_N_YEARS = YEAR - lag(YEAR),
         DELTA_N_EMBASSY_PER_YEAR = DELTA_N_EMBASSY/DELTA_N_YEARS,
         DELTA_POLITY = POLITY - lag(POLITY),
         DELTA_POLITY_PER_YEAR = DELTA_POLITY/DELTA_N_YEARS,
         DELTA_v2x_LIBDEM = v2x_LIBDEM - lag(v2x_LIBDEM),
         DELTA_v2x_LIBDEM_PER_YEAR = DELTA_v2x_LIBDEM/DELTA_N_YEARS,
         DELTA_TOTLIB1 = TOTLIB1 - lag(TOTLIB1),
         DELTA_TOTLIB1_PER_YEAR = DELTA_TOTLIB1/DELTA_N_YEARS,
         DELTA_logGNI = logGNI - lag(logGNI),
         DELTA_logGNI_PER_YEAR = DELTA_logGNI/DELTA_N_YEARS, 
         DELTA_logPOPULATN = logPOPULATN  - lag(logPOPULATN),
         DELTA_logPOPULATN_PER_YEAR = DELTA_logPOPULATN /DELTA_N_YEARS)

# Reduced Models #

mod0_delta_POLITY_PER_YEAR <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR + (1|COUNTRY), data = modelset_delta)
mod0_delta_POLITY <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ POLITY + (1|COUNTRY), data = modelset_delta)
mod0_delta_v2x_LIBDEM <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ v2x_LIBDEM + (1|COUNTRY), data = modelset_delta)
mod0_delta_TOTLIB1 <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ TOTLIB1 + (1|COUNTRY), data = modelset_delta)

# Full Models #

mod1_delta_POLITY_PER_YEAR <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR + DELTA_logGNI + DELTA_logPOPULATN + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY), data = modelset_delta)
mod1_delta_POLITY <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ POLITY + logGNI + logPOPULATN + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY), data = modelset_delta)
mod1_delta_v2x_LIBDEM <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ v2x_LIBDEM + logGNI + logPOPULATN + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY), data = modelset_delta)
mod1_delta_TOTLIB1 <- lmer(DELTA_N_EMBASSY_PER_YEAR ~ TOTLIB1 + logGNI + logPOPULATN + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY), data = modelset_delta)

```
