---
title: "Embassies and Democracy - Results Only"
format: pdf
execute:
  echo: false
  message: false
  warning: false
editor: visual
authors: "Steven Pappas and Gregory J. Matthews"
date: "April 27, 2026"
---

# Summary

# BROAD QUESTION

Broad question: Does the process of democratization within African countries affect the formulation and implementation of African foreign policies.

## THERE ARE THREE DIFFERENT SETS OF STATISTICALLY BASED QUESTIONS (We address only question 1 here):

1.  African democracy and African embassies. Do greater levels of democratization of African countries lead to larger and more diversified embassy networks maintained by African countries overseas? Dependent variable: embassies maintained abroad (yes/no by country) in 1965, 1975, 1985, 1995, 2000, 2005, 2010, 2015, 2020, 2025 (use 2024 for 2025).
2.  African democracy and African trade. Do greater levels of democratization within African countries lead to larger and more diversified levels of trade imports and trade exports by African countries? Dependent variable: \$ amount of imports and exports annually for 1960 to 2022)
3.  African democracy and aid to Africa. Do greater levels of democratization within African countries lead to larger and more diversified levels of foreign aid to African countries? (Dependent variable:\$ amount of aid annually for every country in the world 1960 to 2021).

THUS, THREE DIFFERENT DEPENDENT VARIABLES:

1.  Total number and diversification of African embassies maintained abroad.
2.  Total amount and diversification of African trade imports and trade exports
3.  Total amount and diversification of foreign aid received by African countries

## THREE DIFFERENT VARIABLES OF AFRICAN DEMOCRACY AS INDEPENDENT VARIABLE

Three different variables of democracy (each with different inclusive dates) to use separately in the analyses as the independent variable:

1.  V-Dem democracy variable (1951-2024) Variable name in the dataset: v2x_LIBDEM. It ranges from 0 (worst) to 1 (best).
2.  Polity IV democracy variable (1948-2018) Variable name in the dataset: POLITY. It ranges from -10 (worst) to +10 (best).
3.  Freedom House democracy variable (1972 - 2024) Variable name in the dataset: TOTLIB. It ranges from 1 (best) to 14 (worst). It is a combination of the following two variables, which people sometimes run separately: Civil liberties - Variable name in the dataset: -CIVLIB. It ranges from 1 (best) to 7 (worst). -Political rights: Variable name in the dataset: POLLIB. It ranges from 1 (best) to 7 (worst).

For each of the three democracy variables, will do a series of 4 tests with lags. -Test 1. Change in democracy score (no lag) -Test 2. Change in democracy score (1 year lag) -Test 3. Change in democracy score (2 year lag) -Test 4. Change in democracy score (3 year lag)

## CONTROL VARIABLES RELATED FOR AFRICAN COUNTRIES (AFRICAN FACTORS)

-African GNI OR GNI per capita (logged?) -African Population (size in millions) - Region of Africa (1= North Africa, 2 = East Africa, 3 = Southern Africa, 4= Central Africa, 5 = West Africa) - African Colonial Past (Colpast2) (1 = French, 2 = British, 3 = Portuguese, 4 = Spanish, 5 = Italian, 6 = Belgian, 7 = German, 8 = United States, 9 = Not colony, 10 = unique) - African Ideology (1 = capitalist, 2 = socialist, 3 = Marxist) - African Historical Period - Entire independence era - Cold War era (1945-1989) - Post-Cold War era (1990-present)

## PULL FACTORS—CHARACTERISTICS OF OTHER NON-AFRICAN COUNTRIES OF THE WORLD—JUST FOR THE EMBASSSY QUESTION

-   Level of democracy (Freedom House)
-   Level of democracy (Polity IV)
-   Level of democracy (V-dem) These are in the data set for the African countries, but need to be added for the rest of the world.
-   GNI
-   GNI per capita
-   Population
-   Imports
-   Exports
-   Foreign Aid

FOR THE THREE SETS OF STATISTICALLY BASED QUESTIONS, LET’S START WITH THE EMBASSIES (ABOVE QUESTION #1 FIRST)

## ANSWERING QUESTION #1

To evaluate this question we first created three sets of reduced and full models. Our reduced models sought to evaluate the relationship and the significance of the relationship between a country's embassy count and its democracy score from Freedom House, Polity IV, and V-dem. In these models, democracy score was the only explanatory variable after controlling for the country and year with random effects. The model equation is given below, where $\gamma_{0k}$ represents the random effect for country $k$ and $\gamma_{0t}$ is the random effect for year $t$. We follow the same setup for the lagged models, which go back as far as three years for each democracy score.

# Number of embassy models

## Reduced model

$$
Y_{kt} \sim \text{Poisson}(\lambda_{kt})
$$

$$
\text{log}(\lambda_{kt}) = \beta_0 + \beta_1X_{1kt} + \gamma_{0k} + \gamma_{0t} + \epsilon_{kt}
$$

$$
\gamma_{0k} \sim \text{N}(0, \sigma_k^2)
$$

$$
\gamma_{0t} \sim \text{N}(0, \sigma_t^2)
$$ where $Y_{kt}$ is the number of embassies for country $k$ in year $t$ and $X_{1kt}$ is one of the democracy scores for country $k$ in year $t$. We also considered models where the democracy score as a predictor was lagged by 1, 2, or 3 years (i.e. for a single lag: $\text{log}(\lambda_{kt}) = \beta_0 + \beta_1X_{1k(t-1)} + \gamma_{0k} + \gamma_{0t} + \epsilon_{kt}$ where $X_{1k(t-1)}$ is the democracy score in the prio year.)

As shown in Table 1, in these reduced models none of the democracy scores or their lags display significance at an $\alpha$ = 0.05 confidence level.

## Full model

The full models (results in Table 2) follow a similar setup as the reduced models, but they include additional explanatory variables for the country's GNI, population, region, colonization status after World War II, ideology, and whether the year is during the Cold War. We applied log transformations to GNI and population, since they displayed a right-skewed distribution. We also kept the reduced models' random effects for country and year and followed a similar setup for lagged democracy scores, going back as far as three years. The model equation is given below, with $k$ and $t$ again representing country and year, repsectively.

$$
Y_{kt} \sim \text{Poisson}(\lambda_{kt})
$$

$$
\text{log}(\lambda_{kt}) = \beta_0 + \beta_1X_{1kt} + \ldots + \beta_7X_{7kt} + \gamma_{0k} + \gamma_{0t} + \epsilon_{kt}
$$

$$
\gamma_{0k} \sim \text{N}(0, \sigma_k^2)
$$

$$
\gamma_{0t} \sim \text{N}(0, \sigma_t^2)
$$

where again $Y_{kt}$ is the number of embassies for country $k$ in year $t$ and $X_{1kt}$ is one of the democracy scores for country $k$ in year $t$. The additional $X$'s represent country's GNI, population, region, colonization status after World War II, ideology, and whether the year is during the Cold War. We also considered models where the democracy score as a predictor was lagged by 1, 2, or 3 years (i.e. for a single lag: $\text{log}(\lambda_{kt}) = \beta_0 + \beta_1X_{1k(t-1)} + \gamma_{0k} + \gamma_{0t} + \epsilon_{kt}$ where $X_{1k(t-1)}$ is the democracy score in the prior year.)

Similar to the reduced models, in the full models none of the democracy scores or their lags display significance at an $\alpha$ = 0.05 confidence level. Additionally, none reached a p-value under 0.2. Full results are shown in Table 2.

# Change in number of embassy models

## Reduced model

Next, we sought to evaluate the relationship between a country's yearly change in embassy count by the change in their democracy score. Once again, in this first set of models the random effects for country and year were included . The model equations follow the previously described reduced model setup, however the response variable here is the change in the number of embassies from one year to the next as opposed to the total number of embassies. Therefore, a normal model was used instead of a Poisson model. The details of the model are below:

$$
\Delta_{kt} \sim \text{Normal}(\mu_{kt}, \sigma^2)
$$

$$
\text{log}(\mu_{kt}) = \beta_0 + \beta_1X_{1kt} + \gamma_{0k} + \gamma_{0t} + \epsilon_{kt}
$$

$$
\gamma_{0k} \sim \text{N}(0, \sigma_k^2)
$$

$$
\gamma_{0t} \sim \text{N}(0, \sigma_t^2)
$$ where $\Delta_{kt}$ is the change in the number of embassies from year $t-1$ to $t$, while $\gamma_{0k}$, $\gamma_{0t}$, and X\_{1kt} and are the same as before.

The tables show no significance for any of the changes in democracy score at an $\alpha$ = 0.05 confidence level. The closest is the unlagged democracy score from Polity IV, with a p-value of 0.140. Full results are shown in table 3.

## Full Model

Next, we sought to evaluate the relationship between a country's yearly change in embassy count by the change in their democracy score while accounting for the variables from our previous full model and random effects for country and year. It is important to note that some models only had realized values for before or after the Cold War, so we removed the Cold War indicator in models where it could not explain any variation in our response variable. We also applied the same log transformations to GNI and population to reduce the effect of their right-skew.

The tables show no significance for any of the changes in democracy score at an $\alpha$ = 0.05 confidence level, even when accounting for the full range of factors. The closest is the second lag for the democracy score from Freedom House, with a p-value of 0.102. Full results are shown in Table 4.

## Full model with differenced predictors

Finally, we replicated the setup from our previous full model but applied the same yearly change to the log-transformed GNI and population variables in addition to the democracy score. However, we only lagged the democracy score, so every other variable matched the year the change in embassy was measured. We kept the same random variables for country and year.

Similar to the previous full model, the tables show no significance for any of the changes in democracy score at an $\alpha$ = 0.05 confidence level. The closest is the nonlagged democracy score from V-Dem, with a p-value of 0.171. Full results of these models are shown in Table 5.

```{r message = FALSE, warning=FALSE, echo = FALSE}
library(tidyverse)
library(readxl)
library(lme4)
library(lmerTest)

masterset = read_csv("./data/Master 08-28-2025 AFP excel dataset-3.xlsx - AFRSdata.csv")

restofworld = read_excel("./old_data/Rest of the World.xlsx")

#Data cleaning
#What do we do with -77, -88, and -99?
masterset = masterset %>%
  mutate(across(where(is.numeric), ~na_if(.,-99)),
         across(where(is.numeric), ~na_if(.,-88)),
         across(where(is.numeric), ~na_if(.,-77)),
         across(where(is.numeric), ~na_if(.,-66)),
         COUNTRY = case_when(COUNTRY == "seychelles" ~ "Seychelles",
                             COUNTRY == "sao tome & Principe" ~ "Sao Tome & Principe",
                             .default = COUNTRY))

#Convert commas to periods. 
#it looks like commas are being used as the decimal.  
#Fix the nonsense formatting from excel. 
masterset$GNI <- gsub(",",".",masterset$GNI)
masterset$GNI <- gsub(" ","",masterset$GNI)%>% as.numeric()

masterset$GNI_CAP <- gsub(",",".",masterset$GNI_CAP)
masterset$GNI_CAP <- gsub(" ","",masterset$GNI_CAP)%>% as.numeric()

masterset$POPULATN <- gsub(",",".",masterset$POPULATN)
masterset$POPULATN <- gsub(" ","",masterset$POPULATN) %>% as.numeric()


#Count the embassies
#names(masterset)
masterset <- masterset %>% mutate(N_EMBASSY = select(., C099:C572) %>% rowSums(na.rm = T))

#Preparing data for modeling
masterset <- masterset %>% mutate(YEAR1965 = YEAR - 1965)

#Filter out only years with embassy data
keep_years <- masterset %>% group_by(YEAR) %>% summarize(N_EMBASSY = sum(N_EMBASSY)) %>% filter(N_EMBASSY > 0) %>% pull(YEAR)

#Define lagged variables
modelset <- masterset %>% mutate(GNI = case_when(GNI < 0 ~ NA,.default = GNI),
                                 REGION = case_when(REGION == 1 ~ "North",
                                                    REGION == 2 ~ "East",
                                                    REGION == 3 ~ "South",
                                                    REGION == 4 ~ "Central",
                                                    REGION == 5 ~ "West"))


modelset <- modelset %>% arrange(COUNTRY, YEAR) %>% group_by(COUNTRY)  %>% 
                              mutate(v2x_LIBDEM_lag1 = lag(v2x_LIBDEM,1),
                                 v2x_LIBDEM_lag2 = lag(v2x_LIBDEM,2),
                                 v2x_LIBDEM_lag3 = lag(v2x_LIBDEM,3),
                                 TOTLIB1_lag1 = lag(TOTLIB1,1),
                                 TOTLIB1_lag2 = lag(TOTLIB1,2),
                                 TOTLIB1_lag3 = lag(TOTLIB1,3),
                                 POLITY_lag1 = lag(POLITY,1),
                                 POLITY_lag2 = lag(POLITY,2),
                                 POLITY_lag3 = lag(POLITY,3),
                                 POLITY2_lag1 = lag(POLITY2,1),
                                 POLITY2_lag2 = lag(POLITY2,2),
                                 POLITY2_lag3 = lag(POLITY2,3)
                                 ) %>%  ungroup() %>%   filter(YEAR %in% keep_years & !is.na(COUNTRY)) %>% 
  select(COUNTRY, YEAR, N_EMBASSY, v2x_LIBDEM, POLLIB, TOTLIB1, POLITY, POLITY2,
         CIVLIB, POLLIB,GNI_CAP,GNI, REGION, COLPAST2, IDEOLOGY, POPULATN, v2x_LIBDEM_lag1:POLITY2_lag3) %>%
  mutate(AFR_HIST_PERIOD = case_when(YEAR <= 1989 ~ "Cold War",
                                     YEAR >= 1990 ~ "Post-Cold War"), 
         logGNI = log(GNI, 10),
         logPOPULATN = log(POPULATN, 10),
         COL2 = ifelse(COLPAST2 != 9, "Colony", "Not Colony"),
         REGION = relevel(factor(REGION), ref = "North"),
         YEAR1965 = YEAR-1965)


#Define change in embassies
modelset <- modelset %>% group_by(COUNTRY) %>% arrange(YEAR) %>% 
  mutate(DELTA_N_EMBASSY = N_EMBASSY - lag(N_EMBASSY),
         DELTA_N_YEARS = YEAR - lag(YEAR),
         DELTA_N_EMBASSY_PER_YEAR = DELTA_N_EMBASSY/DELTA_N_YEARS,
         DELTA_POLITY = POLITY - lag(POLITY),
         DELTA_POLITY_PER_YEAR = DELTA_POLITY/DELTA_N_YEARS,
         DELTA_POLITY2 = POLITY2 - lag(POLITY2),
         DELTA_POLITY2_PER_YEAR = DELTA_POLITY2/DELTA_N_YEARS,
         DELTA_v2x_LIBDEM = v2x_LIBDEM - lag(v2x_LIBDEM),
         DELTA_v2x_LIBDEM_PER_YEAR = DELTA_v2x_LIBDEM/DELTA_N_YEARS,
         DELTA_TOTLIB1 = TOTLIB1 - lag(TOTLIB1),
         DELTA_TOTLIB1_PER_YEAR = DELTA_TOTLIB1/DELTA_N_YEARS,
         DELTA_logGNI = logGNI - lag(logGNI),
         DELTA_logGNI_PER_YEAR = DELTA_logGNI/DELTA_N_YEARS, 
         DELTA_logPOPULATN = logPOPULATN  - lag(logPOPULATN),
         DELTA_logPOPULATN_PER_YEAR = DELTA_logPOPULATN /DELTA_N_YEARS)
```

# Exploratory Data Analysis

Below are the distributions of the three democracy variables.

```{r}
#modelset %>% group_by(YEAR, POLLIB) %>% summarize(n = n())
modelset %>% ggplot(aes(x = factor(POLITY))) + geom_bar() + facet_wrap(~YEAR) + theme_bw() + xlab("POLITY")
modelset %>% ggplot(aes(x = factor(POLITY2))) + geom_bar() + facet_wrap(~YEAR) + theme_bw() + xlab("POLITY2")
modelset %>% ggplot(aes(x = factor(TOTLIB1))) + geom_bar() + facet_wrap(~YEAR) + theme_bw() + xlab("TOTLIB1") + scale_x_discrete(breaks = c(2, 5, 8, 11, 14, NA))
modelset %>% ggplot(aes(x = factor(YEAR), y = v2x_LIBDEM)) + geom_boxplot() +theme_bw() + xlab("v2x_LIBDEM")
```

The plot below is the number of embassies over time with each connected line representing a single country.

```{r}
#EDA
modelset %>% ggplot(aes(x = YEAR, y = N_EMBASSY, group = COUNTRY)) + geom_line() + geom_point() + theme_bw() 
```

Next, scatter plots of the number of the democracy variables versus the embassies are plotted and each plot includes a trend line of the relationship.

```{r}
modelset %>% ggplot(aes(x = v2x_LIBDEM, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = v2x_LIBDEM_lag1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = v2x_LIBDEM_lag2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = v2x_LIBDEM_lag3, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()

modelset %>% ggplot(aes(x = POLITY, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = POLITY_lag1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = POLITY_lag2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = POLITY_lag3, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()

modelset %>% ggplot(aes(x = POLITY2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = POLITY2_lag1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = POLITY2_lag2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = POLITY2_lag3, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()

modelset %>% ggplot(aes(x = TOTLIB1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = TOTLIB1_lag1, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = TOTLIB1_lag2, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
modelset %>% ggplot(aes(x = TOTLIB1_lag3, y = N_EMBASSY)) + facet_wrap(~YEAR) +geom_point() + theme_bw() + geom_smooth()
```

```{r echo = T}
#Correlations
#Polity
modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY)$p.val)

modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY_lag1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY_lag1)$p.val)

modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY_lag2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY_lag2)$p.val)

modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY_lag3, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY_lag3)$p.val)

#Polity2
modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY2)$p.val)

modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY2_lag1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY2_lag1)$p.val)

modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY2_lag2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY2_lag2)$p.val)

modelset %>% filter(YEAR < 2020) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,POLITY2_lag3, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,POLITY2_lag3)$p.val)

#v2x_Libdem
modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM)$p.val)

modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM_lag1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag1)$p.val)

modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM_lag2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag2)$p.val)

modelset %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,v2x_LIBDEM_lag3, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,v2x_LIBDEM_lag3)$p.val)

modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1)$p.val)

modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1_lag1, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1_lag1)$p.val)

modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1_lag2, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1_lag2)$p.val)

modelset %>% filter(YEAR > 1965 & YEAR < 2024) %>% group_by(YEAR) %>%
  summarize(cor = cor(N_EMBASSY,TOTLIB1_lag3, use = "pairwise.complete.obs") , pval = cor.test(N_EMBASSY,TOTLIB1_lag3)$p.val)

```

```{r echo = FALSE}
library(lme4)
library(data.table)
library(gt)

mod_TOTLIB1 <- glmer(N_EMBASSY ~ TOTLIB1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag1 <- glmer(N_EMBASSY ~ TOTLIB1_lag1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag2 <- glmer(N_EMBASSY ~ TOTLIB1_lag2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_TOTLIB1_lag3 <- glmer(N_EMBASSY ~ TOTLIB1_lag3 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1, parm = "TOTLIB1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag1, parm = "TOTLIB1_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag2, parm = "TOTLIB1_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_TOTLIB1_lag3, parm = "TOTLIB1_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod_POLITY <- glmer(N_EMBASSY ~ POLITY + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag1 <- glmer(N_EMBASSY ~ POLITY_lag1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag2 <- glmer(N_EMBASSY ~ POLITY_lag2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY_lag3 <- glmer(N_EMBASSY ~ POLITY_lag3 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

POLITY_nolag <- list(
  polity = as.data.frame(coef(summary(mod_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY, parm = "POLITY", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  polity = as.data.frame(coef(summary(mod_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag1, parm = "POLITY_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  polity = as.data.frame(coef(summary(mod_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag2, parm = "POLITY_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  polity = as.data.frame(coef(summary(mod_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY_lag3, parm = "POLITY_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod_POLITY2 <- glmer(N_EMBASSY ~ POLITY2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY2_lag1 <- glmer(N_EMBASSY ~ POLITY2_lag1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY2_lag2 <- glmer(N_EMBASSY ~ POLITY2_lag2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_POLITY2_lag3 <- glmer(N_EMBASSY ~ POLITY2_lag3 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

POLITY2_nolag <- list(
  polity2 = as.data.frame(coef(summary(mod_POLITY2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY2, parm = "POLITY2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  polity2 = as.data.frame(coef(summary(mod_POLITY2_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY2_lag1, parm = "POLITY2_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  polity2 = as.data.frame(coef(summary(mod_POLITY2_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY2_lag2, parm = "POLITY2_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  polity2 = as.data.frame(coef(summary(mod_POLITY2_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_POLITY2_lag3, parm = "POLITY2_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod_v2x_LIBDEM <- glmer(N_EMBASSY ~ v2x_LIBDEM + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag1 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag1 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag2 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag2 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod_v2x_LIBDEM_lag3 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag3 + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM, parm = "v2x_LIBDEM", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag1, parm = "v2x_LIBDEM_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag2, parm = "v2x_LIBDEM_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod_v2x_LIBDEM_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod_v2x_LIBDEM_lag3, parm = "v2x_LIBDEM_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3,
  v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "LIBDEM") ~ "LIBDEM",
                         str_detect(var, "POLITY") ~ "POLITY"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 1: Reduced Model Parameters for **Democracy Scores** and Their **Lags**")
  ) 
#%>%  gtsave("reducedmodel.png")
```

```{r echo = FALSE}

library(data.table)
library(gt)

mod1_TOTLIB1 <- glmer(N_EMBASSY ~ TOTLIB1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

mod1_TOTLIB1_lag1 <- glmer(N_EMBASSY ~ TOTLIB1_lag1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_TOTLIB1_lag2 <- glmer(N_EMBASSY ~ TOTLIB1_lag2 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_TOTLIB1_lag3 <- glmer(N_EMBASSY ~ TOTLIB1_lag3 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

mod1_totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), 
           pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1, parm = "TOTLIB1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), 
           conf_exp_1 = round(exp(conf_1), 3), conf_exp_2 = round(exp(conf_2), 3), 
           confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag1, parm = "TOTLIB1_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag2, parm = "TOTLIB1_lag2", level = 0.95, method = "boot", nsim = 50)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_TOTLIB1_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "TOTLIB1_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_TOTLIB1_lag3, parm = "TOTLIB1_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY <- glmer(N_EMBASSY ~ POLITY + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_POLITY_lag1 <- glmer(N_EMBASSY ~ POLITY_lag1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_POLITY_lag2 <- glmer(N_EMBASSY ~ POLITY_lag2 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_POLITY_lag3 <- glmer(N_EMBASSY ~ POLITY_lag3 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

mod1_POLITY_nolag <- list(
  polity = as.data.frame(coef(summary(mod1_POLITY))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY, parm = "POLITY", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY_lag1 <- list(
  polity = as.data.frame(coef(summary(mod1_POLITY_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY_lag1, parm = "POLITY_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY_lag2 <- list(
  polity = as.data.frame(coef(summary(mod1_POLITY_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY_lag2, parm = "POLITY_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY_lag3 <- list(
  polity = as.data.frame(coef(summary(mod1_POLITY_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY_lag3, parm = "POLITY_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY2 <- glmer(N_EMBASSY ~ POLITY + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_POLITY2_lag1 <- glmer(N_EMBASSY ~ POLITY_lag1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_POLITY2_lag2 <- glmer(N_EMBASSY ~ POLITY_lag2 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_POLITY2_lag3 <- glmer(N_EMBASSY ~ POLITY_lag3 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

mod1_POLITY2_nolag <- list(
  polity2 = as.data.frame(coef(summary(mod1_POLITY2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2, parm = "POLITY2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY2_lag1 <- list(
  polity2 = as.data.frame(coef(summary(mod1_POLITY2_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag1, parm = "POLITY2_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY2_lag2 <- list(
  polity2 = as.data.frame(coef(summary(mod1_POLITY2_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag2, parm = "POLITY2_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_POLITY2_lag3 <- list(
  polity2 = as.data.frame(coef(summary(mod1_POLITY2_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "POLITY2_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_POLITY2_lag3, parm = "POLITY2_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_v2x_LIBDEM <- glmer(N_EMBASSY ~ v2x_LIBDEM + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_v2x_LIBDEM_lag1 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag1 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_v2x_LIBDEM_lag2 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag2 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mod1_v2x_LIBDEM_lag3 <- glmer(N_EMBASSY ~ v2x_LIBDEM_lag3 + logGNI + logPOPULATN  + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR), data = modelset, family = "poisson", control = glmerControl(optimizer = "bobyqa"))

mod1_v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM, parm = "v2x_LIBDEM", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag1, parm = "v2x_LIBDEM_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag2, parm = "v2x_LIBDEM_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

mod1_v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_v2x_LIBDEM_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "v2x_LIBDEM_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|z|)`, 3)),
  conf = data.frame(conf = confint(mod1_v2x_LIBDEM_lag3, parm = "v2x_LIBDEM_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  mod1_totlib_nolag, mod1_totlib_lag1, mod1_totlib_lag2, mod1_totlib_lag3, mod1_POLITY_nolag, mod1_POLITY_lag1, mod1_POLITY_lag2, mod1_POLITY_lag3, mod1_POLITY2_nolag, mod1_POLITY2_lag1, mod1_POLITY2_lag2, mod1_POLITY2_lag3,
  mod1_v2x_LIBDEM_nolag, mod1_v2x_LIBDEM_lag1, mod1_v2x_LIBDEM_lag2, mod1_v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "LIBDEM") ~ "LIBDEM",
                         str_detect(var, "POLITY") ~ "POLITY"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 2: Full Model Parameters for **Democracy Scores** and Their **Lags**")
  ) 
#%>% gtsave("fullmodel.png")
```

```{r}

# Data #
modelset_delta <- modelset %>% group_by(COUNTRY) %>% arrange(YEAR) %>% 
  mutate(DELTA_N_EMBASSY = N_EMBASSY - lag(N_EMBASSY),
         DELTA_N_YEARS = YEAR - lag(YEAR),
         DELTA_N_EMBASSY_PER_YEAR = DELTA_N_EMBASSY/DELTA_N_YEARS,
         DELTA_POLITY = POLITY - lag(POLITY),
         DELTA_POLITY_PER_YEAR = DELTA_POLITY/DELTA_N_YEARS,
         DELTA_POLITY_PER_YEAR_lag1 = lag(DELTA_POLITY_PER_YEAR),
         DELTA_POLITY_PER_YEAR_lag2 = lag(DELTA_POLITY_PER_YEAR, 2),
         DELTA_POLITY_PER_YEAR_lag3 = lag(DELTA_POLITY_PER_YEAR, 3),
         
         DELTA_POLITY2_PER_YEAR_lag1 = lag(DELTA_POLITY2_PER_YEAR),
         DELTA_POLITY2_PER_YEAR_lag2 = lag(DELTA_POLITY2_PER_YEAR, 2),
         DELTA_POLITY2_PER_YEAR_lag3 = lag(DELTA_POLITY2_PER_YEAR, 3),
         
         DELTA_v2x_LIBDEM = v2x_LIBDEM - lag(v2x_LIBDEM),
         DELTA_v2x_LIBDEM_PER_YEAR = DELTA_v2x_LIBDEM/DELTA_N_YEARS,
         DELTA_v2x_LIBDEM_PER_YEAR_lag1 = lag(DELTA_v2x_LIBDEM_PER_YEAR),
         DELTA_v2x_LIBDEM_PER_YEAR_lag2 = lag(DELTA_v2x_LIBDEM_PER_YEAR, 2),
         DELTA_v2x_LIBDEM_PER_YEAR_lag3 = lag(DELTA_v2x_LIBDEM_PER_YEAR, 3),
         DELTA_TOTLIB1 = TOTLIB1 - lag(TOTLIB1),
         DELTA_TOTLIB1_PER_YEAR = DELTA_TOTLIB1/DELTA_N_YEARS,
         DELTA_TOTLIB1_PER_YEAR_lag1 = lag(DELTA_TOTLIB1_PER_YEAR),
         DELTA_TOTLIB1_PER_YEAR_lag2 = lag(DELTA_TOTLIB1_PER_YEAR, 2),
         DELTA_TOTLIB1_PER_YEAR_lag3 = lag(DELTA_TOTLIB1_PER_YEAR, 3),
         DELTA_logGNI = logGNI - lag(logGNI),
         DELTA_logGNI_PER_YEAR = DELTA_logGNI/DELTA_N_YEARS, 
         DELTA_logPOPULATN = logPOPULATN  - lag(logPOPULATN),
         DELTA_logPOPULATN_PER_YEAR = DELTA_logPOPULATN /DELTA_N_YEARS)

## ---- Reduced Delta Models With Lags ----

mod0_delta_POLITY_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_POLITY_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag1 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_POLITY_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag2 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_POLITY_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag3 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)

mod0_delta_POLITY2_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_POLITY2_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag1 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_POLITY2_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag2 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_POLITY2_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag3 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)

mod0_delta_v2x_LIBDEM_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_v2x_LIBDEM_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag1 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_v2x_LIBDEM_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag2 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_v2x_LIBDEM_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag3 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)

mod0_delta_TOTLIB1_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_TOTLIB1_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag1 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_TOTLIB1_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag2 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)
mod0_delta_TOTLIB1_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag3 + (1|COUNTRY) + (1|YEAR), 
  data = modelset_delta
)

## ---- Table Data (Reduced Delta Models With Lags) ----

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_TOTLIB1_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), 
           pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_TOTLIB1_PER_YEAR, parm = "DELTA_TOTLIB1_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), 
           conf_exp_1 = round(exp(conf_1), 3), conf_exp_2 = round(exp(conf_2), 3), 
           confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_TOTLIB1_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_TOTLIB1_PER_YEAR_lag1, parm = "DELTA_TOTLIB1_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_TOTLIB1_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_TOTLIB1_PER_YEAR_lag2, parm = "DELTA_TOTLIB1_PER_YEAR_lag2", level = 0.95, method = "boot", nsim = 50)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_TOTLIB1_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_TOTLIB1_PER_YEAR_lag3, parm = "DELTA_TOTLIB1_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  polity = as.data.frame(coef(summary(mod0_delta_POLITY_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY_PER_YEAR, parm = "DELTA_POLITY_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  polity = as.data.frame(coef(summary(mod0_delta_POLITY_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY_PER_YEAR_lag1, parm = "DELTA_POLITY_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  polity = as.data.frame(coef(summary(mod0_delta_POLITY_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY_PER_YEAR_lag2, parm = "DELTA_POLITY_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  polity = as.data.frame(coef(summary(mod0_delta_POLITY_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY_PER_YEAR_lag3, parm = "DELTA_POLITY_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  polity2 = as.data.frame(coef(summary(mod0_delta_POLITY2_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY2_PER_YEAR, parm = "DELTA_POLITY2_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  polity2 = as.data.frame(coef(summary(mod0_delta_POLITY2_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY2_PER_YEAR_lag1, parm = "DELTA_POLITY2_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  polity2 = as.data.frame(coef(summary(mod0_delta_POLITY2_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY2_PER_YEAR_lag2, parm = "DELTA_POLITY2_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  polity2 = as.data.frame(coef(summary(mod0_delta_POLITY2_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_POLITY2_PER_YEAR_lag3, parm = "DELTA_POLITY2_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_v2x_LIBDEM_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_v2x_LIBDEM_PER_YEAR, parm = "DELTA_v2x_LIBDEM_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_v2x_LIBDEM_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_v2x_LIBDEM_PER_YEAR_lag1, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_v2x_LIBDEM_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_v2x_LIBDEM_PER_YEAR_lag2, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod0_delta_v2x_LIBDEM_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod0_delta_v2x_LIBDEM_PER_YEAR_lag3, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3,
  v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "LIBDEM") ~ "LIBDEM",
                         str_detect(var, "POLITY") ~ "POLITY"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 3: Delta Response Reduced Model for **Democracy Scores** and Their **Lags**")
  )
#%>% gtsave("deltareducedmodel.png")

```

```{r}

## ---- Full Models With Non-Delta Predictors (Besides Main Predictor) ----

mod1_delta_POLITY_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR + logGNI + logPOPULATN + REGION + COL2 +
  factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_POLITY_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag1 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_POLITY_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag2 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_POLITY_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag3 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)

mod1_delta_POLITY2_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR + logGNI + logPOPULATN + REGION + COL2 +
  factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_POLITY2_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag1 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_POLITY2_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag2 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_POLITY2_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag3 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)

mod1_delta_v2x_LIBDEM_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR + logGNI + logPOPULATN + REGION + 
  COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_v2x_LIBDEM_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag1 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_v2x_LIBDEM_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag2 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_v2x_LIBDEM_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag3 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)

mod1_delta_TOTLIB1_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR + logGNI + logPOPULATN + REGION + 
  COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_delta_TOTLIB1_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag1 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY) + (1|YEAR),
  data = modelset_delta
)
mod1_delta_TOTLIB1_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag2 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY) + (1|YEAR),
  data = modelset_delta
)
mod1_delta_TOTLIB1_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag3 + logGNI + logPOPULATN + REGION +
  COL2 + factor(IDEOLOGY) + (1|COUNTRY) + (1|YEAR),
  data = modelset_delta
)

## ---- Table Data (Full Models With Non-Delta Predictors Besides Main)

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_TOTLIB1_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), 
           pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_TOTLIB1_PER_YEAR, parm = "DELTA_TOTLIB1_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), 
           conf_exp_1 = round(exp(conf_1), 3), conf_exp_2 = round(exp(conf_2), 3), 
           confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_TOTLIB1_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_TOTLIB1_PER_YEAR_lag1, parm = "DELTA_TOTLIB1_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_TOTLIB1_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_TOTLIB1_PER_YEAR_lag2, parm = "DELTA_TOTLIB1_PER_YEAR_lag2", level = 0.95, method = "boot", nsim = 50)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_TOTLIB1_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_TOTLIB1_PER_YEAR_lag3, parm = "DELTA_TOTLIB1_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  polity = as.data.frame(coef(summary(mod1_delta_POLITY_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY_PER_YEAR, parm = "DELTA_POLITY_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  polity = as.data.frame(coef(summary(mod1_delta_POLITY_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY_PER_YEAR_lag1, parm = "DELTA_POLITY_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  polity = as.data.frame(coef(summary(mod1_delta_POLITY_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY_PER_YEAR_lag2, parm = "DELTA_POLITY_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  polity = as.data.frame(coef(summary(mod1_delta_POLITY_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY_PER_YEAR_lag3, parm = "DELTA_POLITY_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  polity2 = as.data.frame(coef(summary(mod1_delta_POLITY2_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY2_PER_YEAR, parm = "DELTA_POLITY2_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  polity2 = as.data.frame(coef(summary(mod1_delta_POLITY2_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY2_PER_YEAR_lag1, parm = "DELTA_POLITY2_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  polity2 = as.data.frame(coef(summary(mod1_delta_POLITY2_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY2_PER_YEAR_lag2, parm = "DELTA_POLITY2_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  polity2 = as.data.frame(coef(summary(mod1_delta_POLITY2_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_POLITY2_PER_YEAR_lag3, parm = "DELTA_POLITY2_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_v2x_LIBDEM_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_v2x_LIBDEM_PER_YEAR, parm = "DELTA_v2x_LIBDEM_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_v2x_LIBDEM_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_v2x_LIBDEM_PER_YEAR_lag1, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_v2x_LIBDEM_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_v2x_LIBDEM_PER_YEAR_lag2, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_delta_v2x_LIBDEM_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_delta_v2x_LIBDEM_PER_YEAR_lag3, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3,
  v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "LIBDEM") ~ "LIBDEM",
                         str_detect(var, "POLITY") ~ "POLITY"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 4: Delta Response Full Model for **Democracy Scores** and Their **Lags**")
  ) 
#%>% gtsave("nondeltafullmodel.png")

```

```{r}

## ---- Full Models With All Delta Predictors ----

mod1_alldelta_POLITY_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_POLITY_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag1 + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_POLITY_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag2 + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_POLITY_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY_PER_YEAR_lag3 + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)

mod1_alldelta_POLITY2_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_POLITY2_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag1 + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_POLITY2_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag2 + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_POLITY2_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_POLITY2_PER_YEAR_lag3 + DELTA_logGNI_PER_YEAR + DELTA_logPOPULATN_PER_YEAR +
  REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)

mod1_alldelta_v2x_LIBDEM_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag1 + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) +
  (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag2 + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) +
  (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_v2x_LIBDEM_PER_YEAR_lag3 + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) +
  (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)

mod1_alldelta_TOTLIB1_PER_YEAR <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) + factor(AFR_HIST_PERIOD) +
  (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_TOTLIB1_PER_YEAR_lag1 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag1 + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_TOTLIB1_PER_YEAR_lag2 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag2 + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)
mod1_alldelta_TOTLIB1_PER_YEAR_lag3 <- lmer(
  DELTA_N_EMBASSY_PER_YEAR ~ DELTA_TOTLIB1_PER_YEAR_lag3 + DELTA_logGNI_PER_YEAR +
  DELTA_logPOPULATN_PER_YEAR + REGION + COL2 + factor(IDEOLOGY) + (1|COUNTRY)+ (1|YEAR),
  data = modelset_delta
)

## ---- Table Data (Full Models With Delta Predictors) ----

totlib_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_TOTLIB1_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), 
           pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_TOTLIB1_PER_YEAR, parm = "DELTA_TOTLIB1_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), 
           conf_exp_1 = round(exp(conf_1), 3), conf_exp_2 = round(exp(conf_2), 3), 
           confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_TOTLIB1_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_TOTLIB1_PER_YEAR_lag1, parm = "DELTA_TOTLIB1_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_TOTLIB1_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_TOTLIB1_PER_YEAR_lag2, parm = "DELTA_TOTLIB1_PER_YEAR_lag2", level = 0.95, method = "boot", nsim = 50)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

totlib_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_TOTLIB1_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_TOTLIB1_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_TOTLIB1_PER_YEAR_lag3, parm = "DELTA_TOTLIB1_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_nolag <- list(
  polity = as.data.frame(coef(summary(mod1_alldelta_POLITY_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY_PER_YEAR, parm = "DELTA_POLITY_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag1 <- list(
  polity = as.data.frame(coef(summary(mod1_alldelta_POLITY_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY_PER_YEAR_lag1, parm = "DELTA_POLITY_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag2 <- list(
  polity = as.data.frame(coef(summary(mod1_alldelta_POLITY_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY_PER_YEAR_lag2, parm = "DELTA_POLITY_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY_lag3 <- list(
  polity = as.data.frame(coef(summary(mod1_alldelta_POLITY_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY_PER_YEAR_lag3, parm = "DELTA_POLITY_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_nolag <- list(
  polity2 = as.data.frame(coef(summary(mod1_alldelta_POLITY2_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY2_PER_YEAR, parm = "DELTA_POLITY2_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag1 <- list(
  polity2 = as.data.frame(coef(summary(mod1_alldelta_POLITY2_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY2_PER_YEAR_lag1, parm = "DELTA_POLITY2_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag2 <- list(
  polity2 = as.data.frame(coef(summary(mod1_alldelta_POLITY2_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY2_PER_YEAR_lag2, parm = "DELTA_POLITY2_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

POLITY2_lag3 <- list(
  polity2 = as.data.frame(coef(summary(mod1_alldelta_POLITY2_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_POLITY2_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_POLITY2_PER_YEAR_lag3, parm = "DELTA_POLITY2_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_nolag <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_v2x_LIBDEM_PER_YEAR))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_v2x_LIBDEM_PER_YEAR, parm = "DELTA_v2x_LIBDEM_PER_YEAR", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag0") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag1 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag1))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag1") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag1, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag1", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag1") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag2 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag2))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag2") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag2, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag2", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag2") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

v2x_LIBDEM_lag3 <- list(
  totlib1 = as.data.frame(coef(summary(mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag3))) %>%
    rownames_to_column(var = "var") %>%
    filter(var == "DELTA_v2x_LIBDEM_PER_YEAR_lag3") %>%
    mutate(Estimate = round(Estimate, 3), Estimate_exp = exp(Estimate), pval = round(`Pr(>|t|)`, 3)),
  conf = data.frame(conf = confint(mod1_alldelta_v2x_LIBDEM_PER_YEAR_lag3, parm = "DELTA_v2x_LIBDEM_PER_YEAR_lag3", level = 0.95)) %>%
    rownames_to_column(var = "var") %>%
    mutate(conf_1 = round(conf.2.5.., 3), conf_2 = round(conf.97.5.., 3), conf_exp_1 = round(exp(conf_1), 3), 
           conf_exp_2 = round(exp(conf_2), 3), confidence = paste0(conf_1, ", ", conf_2),
           confidence_exp = paste0(conf_exp_1, ", ", conf_exp_2))
) %>% reduce(merge, by = "var") %>%
  mutate(lag = "lag3") %>%
  select(var, lag, Estimate, Estimate_exp, pval, confidence, confidence_exp)

table_data = list(
  totlib_nolag, totlib_lag1, totlib_lag2, totlib_lag3, POLITY_nolag, POLITY_lag1, POLITY_lag2, POLITY_lag3, POLITY2_nolag, POLITY2_lag1, POLITY2_lag2, POLITY2_lag3,
  v2x_LIBDEM_nolag, v2x_LIBDEM_lag1, v2x_LIBDEM_lag2, v2x_LIBDEM_lag3
) %>%
  rbindlist() %>%
  mutate(var = case_when(str_detect(var, "TOTLIB1") ~ "TOTLIB1",
                         str_detect(var, "POLITY2") ~ "POLITY2",
                         str_detect(var, "LIBDEM") ~ "LIBDEM",
                         str_detect(var, "POLITY") ~ "POLITY"),
         Estimate_exp = round(Estimate_exp, 3))

table_data %>%
  gt(rowname_col = "var", groupname_col = "lag") %>%
  tab_options(row_group.as_column = T) %>%
  cols_label(
    Estimate = md("$\\hat{\\beta}$"),
    Estimate_exp = md("$e^{\\hat{\\beta}}$"),
    pval = md("$p$"),
    confidence = md("$\\hat{\\beta}: 95\\% CI$"),
    confidence_exp = md("$e^{\\hat{\\beta}}: 95\\% CI$")
  ) %>%
  cols_align(
    align = "center"
  ) %>%
  tab_header(
    title = md("Table 5: Delta Response Delta Predictors Full Model for **Democracy Scores** and Their **Lags**")
  ) 
#%>% gtsave("deltafullmodel.png")

```

# Appendix

```{r echo = T}
#Embassy models
summary(mod_TOTLIB1)
summary(mod1_TOTLIB1)

summary(mod_POLITY)
summary(mod1_POLITY)

summary(mod_POLITY2)
summary(mod1_POLITY2)

summary(mod_v2x_LIBDEM)
summary(mod1_v2x_LIBDEM)

#Change in Embassy Models
summary(mod0_delta_TOTLIB1_PER_YEAR)
summary(mod1_delta_TOTLIB1_PER_YEAR)

summary(mod0_delta_POLITY_PER_YEAR)
summary(mod1_delta_POLITY_PER_YEAR)

summary(mod0_delta_POLITY2_PER_YEAR)
summary(mod1_delta_POLITY2_PER_YEAR)

summary(mod0_delta_v2x_LIBDEM_PER_YEAR)
summary(mod1_delta_v2x_LIBDEM_PER_YEAR)

```
